---
title: "Solutions for the Short-Term Economic Impacts of Marine Reserves"
author: "Dan Ovando, Dawn Dougherty, Jono Wilson"
date: "July 9, 2015"
output:
  html_document:
    fig_align: center
    fig_caption: yes
    fig_height: 6
    fig_width: 8
  pdf_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 8
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 8
number_sections: yes
csl: fish-and-fisheries.csl
bibliography: MPA Benefits.bib
toc: yes
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.path='Figs/', echo=FALSE, warning=FALSE, message=FALSE)
```
```{r}
library(gridExtra)
library(ggplot2)
ModelRun <- 'Full Grid 2.1'

load(paste('Results/',ModelRun,'/NutsPlots.Rdata',sep = ''))

```

# Note

 * Play with the discount rate to include the biomass stuff, to show that the biomass goes up
 * The most robust reserve 
 * Cap interest rate at 25%
 * Loans 
 * Show trajectory with and without the price increase
 * Put cartoon back in 
 * fig 4 out
 * make figure 5 colored by timing to benefit 
 *
 
 1. Cartoon
 2. Discount
 3. NPB
 4. Trajectories
 5. Price
 6. Loan
 7. Cross species
 
 

# Abstract

Well-managed fisheries are critical for supporting healthy ocean ecosystems, coastal livelihoods, and food security for millions of people. Many communities lack the resources to implement effective fisheries management. No-take marine reserves are a relatively simple tool to conserve biodiversity and provide fishery benefits. Although empirical examples of fishery benefits from reserves are becoming more prevalent, the short-term economic impacts of establishing marine reserves are rarely considered (note that for this paper, the we refer soley to fishing when we consider economic impacts).  In this paper we simulate fisheries for six species commonly caught in coastal fisheries in order to demonstrate the time required for a no-take reserve to provide a net improvement in the economic wellbeing of a fishing community. Our results show that while conservation benefits accrue rapidly, more than a decade is often required to provide net fisheries benefits, even under circumstances favorable for reserves. We explore a suite of strategies for mitigating these short-term economic losses, including flexible reserve designs, rights-based management, and loans. Our results indicate that combinations of these strategies can greatly reduce the short-term economic impacts of no-take marine reserves. Our findings provide mechanisms for improving the viability of no-take marine reserves as tools for fisheries management and conservation. 

# Introduction

More than 260 million people across the globe earn their livelihood in fishing related industries [@Teh2014]. Fish is a primary source of protein to over one billion people [@FAO2011]. Yet the sustainability of the fishing industry and the potential for wild capture fisheries to indefinitely feed a growing population is dependent on the implementation and enforcement of effective systems of governance and management. No-take marine reserves (hereafter reserves), areas set off-limits to fishing, are a widely used tool for protecting fish populations and are known to provide key conservation benefits that can improve ecosystem services to coastal environments. Conservation benefits of marine reserves include the maintenance of spatial population structure of fish stocks [@Berkeley2004; @White2008; @Rassweiler2012], protection of essential fish habitat, increased species diversity and fish biomass [@Lester2009], and can serve as reference areas to set local management regulations and disentangle the effects of fishing from environmental variability [@Wilson2013]. Enhanced biological production inside reserves can benefit adjacent fisheries through adult spillover [@Roberts1991; @Allison1998; @McClanahan2008] and larval export [@Cudney-Bueno2009; @Pelc2010], especially in situations where the size of the reserve is larger than the adult home range size, and smaller than the scale of larval dispersal [@Gerber2003]. Reserves can also serve as a hedge against changes in environmental conditions [@Stefansson2005; @Costello2008)] and as an effective means of protecting spatially complex marine populations [@White2008; @Rassweiler2012]. 

Marine reserves are increasingly proposed as a mechanism for simultaneously contributing to strong conservation outcomes and improving the productivity of fisheries [@Gaines2010]. This argument is often made in the context of developing world fisheries, which may have little capacity to perform more complex fishery management practices (such as quotas, size limits, or effort restrictions)[@Hollans1996]. In fact, reserves have a long history as fishery management tools in many island nations [@Johannes1978; @Johannes2002]. However, the ability marine reserves to provide fishery benefits is dependent on a suite of factors, including the size of reserve relative to the home range size of the species, the dispersal potential, geographic extent of the stock, as well as the status of the fishery prior to implementation of reserves [@Sanchirico2001; @Costello2008; @White2008; @Rassweiler2012; @Sanchirico2006; @Smith2003]. Moreover, the implementation of marine reserves necessarily reduces the spatial extent of the fishery, often limiting take in prime fishing grounds and concentrating effort into smaller regions of the coast [@Halpern2004]. 

The potential and challenges of utilizing reserves as fishery management tools have been well studies then [@Hilborn2004], though it is worth noting that the vast majority of this work is simulation based, and little empirical evidence of the fishery impacts of reserves is available [see @Fletcher2014 for an empirical paper that found no evidence of enhanced fishery production from the Great Barrier Reef marine reserve]. There is a critical gap in the the literature concerning fisheries and reserves though; the economic impacts over time. Nearly all of the published research on the topic has considered the long-term (or equilibrium) economic impacts of implementing a marine reserve. However, while the long-term impacts are critical to understanding the interactions between reserves and fisheries, from the perspective of fishing community's the short-term impacts may be of much greater consequence. Depending on the time horizon that a community is able or willing to consider, a reserve that provides long-term fishery beneifts may provide no practical benefit to today's fishers and decision makers. Alternatively, even in conditions in which a community will perceive benefits in the future, they may have to endure years of reduced fishing income and food until those benefits arrive.These short-term consequences of reserves can have profound implications on the financial health and food security of fishing communities, affecting local support and buy in for enforcement policies, trust in management and supporting organizations, and ultimately the sustainability of the fishery itself. 

Brown et al. [@-Brown2014] provides an important contribution to our understanding ot the short-term impacts of marine reserves. They illustrate that their are often important tradeoffs between short-term and long-term economic fishing benefits from reserves, and that alternative strategies for designing those reserves (how large they are and how that size changes over time) can dramatically affect the short-term economic effects of a reserve. 

[@-Brown2014] launches an imporatant discussion on the ways in we might choose to design reserves in order to provide fishery benefits, and the ways in which the consequences of those choices can be communicated to fishing communities. In particular, they point out that reserves designed around long-term benefits have substantial short-term costs. Our paper builds of array of design and finance based solutions to mitigating short-term economic impacts created by marine reserves. We ask: 
    1. How does the size of a reserve affect the magnitude and timing of net fishery benefits?
    2. How capable are design and financial solutions of offsetting short-term economic losses?
    3. What reserve strategy maximizes a community's net benefit?
    
We find that for many reef-fish species, reserves may struggle to provide net fishing benefits at a time scale that is of value to fishing communities, but that design and financial mechanisms show strong potential for offsetting these losses.

# Methods

## Operating Model

We analyzed 6 different species, intended to capture a range of life-history traits of species often targeted by developing country fisheries (see supplementary online material for species and life history parameters). Our model is single species, age-structured and assumed to be closed with respect to larval and adult emigration . The spatial configuration of the fishery includes 100 unique patches connected by larval and adult movement. The model tracks stock biomass, fishery yields, and net present benefits each year. 

```{r}

LifeHistories <- read.csv('Inputs/Life History Inputs.csv',stringsAsFactors = F)

LifeVars <- c('CommName','SciName','Range','MaxAge','m','k','Linf','t0','AgeMa50','LengthMa50','BH.Steepness','wa','wb','DDForm','Source)

LifeTable <- LifeHistories[, LifeVars]


```

The number of fish in patch i at age a at the beginning of year t+1 is

(1) $N_{i,a,t+1} = R_{i,t+1}$ if *a = 0*

(2) $N_{i,a,t+1} = N_{i,a-1,t}e^{-M-F_{i,t}\upsilon_{a-1}}$  if $1 \leq a < x$

(3) $N_{i,a,t+1} = N_{i,x-1,t}e^{-M-F_{i,t}\upsilon_{x-1}} + N_{i,x,t}e^{-M-F_{i,t}\upsilon_{x}}$  if $a = x$

where *R~i,t~*is the recruitment in patch *i* in year *t*, *F~i,t~* is the instantaneous fishing mortality in patch *i* in year *t*, $\upsilon_{a}$ is the selectivity of the fishing gear for a fish at age *a*,  *M* is the instantaneous natural mortality, and *x* is the maximum age recorded in the model (the plus group). This model assumes that the biological parameters of each species are homogeneous across space and time.

The simulations begin at an unfished equilibrium using a specified unfished initial recruitment in each patch *i*, *R~i,0~* such that

(4) $N_{i,a} = R_{i,0}$ if *a = 0*

(5) $N_{i,a} = N_{i,a-1}e^{-M}$  if $1 \leq a < x$

(6) $N_{i,a} = \frac{N_{i,x-1}e^{-M}}{1-e^{-M}}$  if $a = x$

The population is then fished down at a specified open access harvest rate in both patches to equilibrium conditions. We set this rate such that biomass over biomass at maximum sustainable yield (B/B~MSY~) is equal to 0.25 at equilibrium, representing an overfished fishery. We chose this level as the benefits of reserve formation were positively (and relatively linearly) related to the degree of overfishing. Starting at an overfished state then provides an optimistic estimation of the potential benefits of reserve formation.  

The average length (*l~a~*) of fish in each age class is calculated using a von Bertalanffy growth equation

(7) $l_{a} = L_{inf}(1-e^{-k(t-t_{0})})$

and then converted to average weight (*w~a~*) using:

(8) $w_{a}=b_{1}l_{a}^{b_{2}}$

We assume habitat quality to be the same in all patches.  Adult movement at each time step among the 100 patches is then calculated using a Gaussian dispersal kernel 

(9) $p_{i,j}=e^{\frac{-d_{i,j}^{2} }{2\sigma_{A}^{2}}}$

where *p~i,j~*  is the proportion of fish moving from area *i* to area *j*,  and *d~i,j~* is the distance between area *i* and area *j*. The model parameter $\sigma_{A}$ defines the movement range for the species. We wrap movement in order to remove edge effects. The relative proportions are then normalized so that the total proportion of fish moving from area *i* to any area sum to one. The number of fish in each age group one and older after movement are then

(10) $N_{i,a,t} = \sum^{100}_{j=1} N_{j,a,t}p_{i,j}$

To calculate recruitment each year, in each pach... **We use methods described in Babcock & MacCall [-@Babcock2011] XXX**

## Fishery Dynamics

The catch in each patch at each time step is calculated as

(11) $Y_{i,t} = \sum_{a}(N_{i,a,t}e^{-F_{i,t}\upsilon_{a}})$ 

We assume a closed population of fishers, where the number of fishers does not change with the implementation of a reserve (no emigration or immigration of boats), such that the effort from the reserve area is displaced to the fished area. This is intended to reflect a subsistence style fishery, with few alternative livelihoods besides fishing. Fishing effort is scaled by the relative commercial biomass,$\bar{B}_{i}$, in each patch where

(12) $\bar{B}_{i}= \frac{B_{i}}{\sum_{i}B_{i}}$

(13) $F_{i,t}=F_{pNTZ}(1+P_{NTZ})\bar{B}_{i}$

Where *F~pNTZ~* is the total possible instantaneous fishing pressure in the patch before the implementation of the reserve, and *P~NTZ~* is the fraction of patches that are in a reserve. 

## Reserve Implementation

We simulate a series of reserve implementation scenarios using the above operating model and fleet dynamics. A given scenario is defined by an terminal reserve size (% of area in a reserve), an "intercept" (% size of the terminal reserve in year 1), and a "slope" (% of run years at which the reserve reaches terminal size). In effect then we allow the final size, initial size, and rate at which the reserve reaches its final size to vary. We apply a subset grid of possible combinations of reserve size, intercept, and slope to each of the 6XX species included in this paper, providing an outline of the potential outcomes of reserve implementation. 

## Metrics

Throughout each scenario we keep track of live biomass of fish in the water and fishery yields over time. Net present balance (NPB) is our primary metric of performance, where NPB represents the cumulative yield benefits of a given reserve strategy relative to the status quo, calculated as

(14) $NPB_{s} = \sum^{T}_{t=0} \frac{Y_{s,t}-Y_{q}}{(1+r)^{t}}$

for any given species, where *t* is time, *Y* represents fishing yields, *s* is reserve implementation strategy, *q* is the status quo, *r* is the economic discount rate, and *T* is a specified number of years after reserve implementation in which *NPB* is calculated and compared across scenarios and species. We calculate the year at which NPB surpasses zero (increased benefits have compensated for short-term losses). NPB is an important output, since it reflects the net benefit that a community perceives from a given reserve strategy, relative to their benefit without the reserve. Alternatively, present balance (PB), the discounted difference between yields of a given reserve strategy and the status quo in year t, while important and a commonly presented metric, may not be as meaningful to a community (e.g. a 1 ton improvement over the status quo in year 10 of a reserve strategy may be of little value if 1,000 tons have been lost in years 1 through 9; see Fig.1 for an illustration of these concepts). 

![Illustration of the trajectory of net benefits following a reserve](Cartoon.pdf)

## Financial Mechanisms

We also analyze two potential financial mechanisms for offsetting short-term fishery losses stemming from the reserve; a loan system and a value added system. The total relative loss in yields experienced by the fishery for a given scenario *s* is 

*Note I think I've now tured r to zero, I think that's better*

(14) $O_{s} = -\sum^{T}_{t=0} min(0,\frac{Y_{s,t}-Y_{q}}{(1+r)^{t}})$

Where *O~a* is the amount of yield lost relative to the status quo. Under the loan strategy, a non-governmental organization, government, or private investor could provide a community with a loan to offset the initial losses from implementing a reserve, with a goal of being repaid by the future fishery benefits resulting from enhanced fishery productivity. The fishing community requests a loan totalling *O~a~*. The surplus available to pay the loan back over time are equal to 

(15) $S_{s} = -\sum^{T}_{t=0} max(0,\frac{Y_{s,t}-Y_{q}}{(1+r)^{t}})$
 
 Where *S~s~* is the total surplus in yields experienced by the fishery for a given scenario *s* over what the fishery would have experienced under the status quo. We then use the *optim* package in *R* [@RCoreTeam2015] to estimate the highest interest rate (%) that the community could afford in order to pay back a 10-year loan of magnitude *O~s~* using surplus *S~s~*. The higher the maximum potential interest rate, the more viable the loan is. 
 
For the value increase scenario, we implicitly assume a status quo value of $1 per unit weight (though this is an arbitraty choice that does not in fact matter). We then ask by what percent the value of the catch caught under a given scenario *s* would have to increase in order to completely offset *O~s~*. This is calculated as

(16) $P_{s} = 100(\sum_{t=0}^{T} \frac{Y_{q}}{Y_{q}+min(0,Y_{s,t}-Y_{q})}(1+r)^{-t}-1))$

Reserves often face competing obejctives between long-term and short-term benefits. This can be empirically illustrated by considering the net present benefits of the reserve over time with a discount rate *r* of 0 (long-term planner, $Y_{r_{0}}$) vs. the net present benefits of the reserve over time with a discount rate *r* > 0 (in this case we consider 0.1XX, $Y_{r_{0.1}}$)). In order to consider the relative utility of a given reserve strategy *s* we assign a weighting parameter $\alpha$ that can take any value from 0 to 1, such that total utillity *U* is calculated as

(17) $U_{s} = \alpha(\frac{Y_{r_{0},s}}{\sum_{s}Y_{r_{0},s}}) + (1-\alpha)(\frac{Y_{r_{0.1},s}}{\sum_{s}Y_{r_{0.1},s}})$

This allows us to calculate utility focused solely on long-term benefits ($\alpha$=1), short-term benefits ($\alpha$=0), or any relative weighting in between. 

# Results

## Discount Rate
```{r, fig.cap='NPB trajectories under optimal reserve scenario under different discount rates'}

discount_rate_plot

```

## Sensitivity to Design

Results up to here show that yes reserves can take time to provide benefits if at all, design can help a bit, multi-species adds another layer though many species do just about as well with similar species reserves as they do with their optimal one. 

We first consider how sensitive our results are to implementing the incorrect terminal reserve size. Or in other words, we consider our results under a range of terminal reserve sizes, and ask how sensitive our results are to being in a particular window. If it's small, unlikely that we'll find it in the real world.  

* For bumphead, grouper, and snapper peak NPB occurs at around 10% reserve size, neagative by about 20%. Emperor much larger. Blacknose shark and trevally not possible. This suggests that reserves less than 20% viable from an NPB perspective for many common species, not so much beyond that. But, it's not knife edged (optimal or bust)

```{r, fig.cap= 'NPB under possible terminal reserve sizes for each species'}
static_NPB_plot
```

So, under static scenario we see that NPB is somewhat sensitive to terminal reserve size, but not extremely; for a general class of reserves under 20% seems possible, though the scale of it matters. What about other metrics?

* We see that even though positive NPB is possible up to the sizes seen in Fig.4, it takes a long time to achieve. So, while the ability to break even at all is somewhat insensitive to reserve size, the amount of time required increases almost exponentially in reserve size.

Our results show though that while design has some potential for offsetting the short-term economic impacts of reserves, there are substantial challenges for relying solely on design as a solution. First, we see that reserves greater than 25% have very little chance of providing positive NPB for the majority of common reef fish studied here (Fig.5). However, numerous studies suggest that from a conservation perspective marine reserves covering 25-30% of range are a minimum recommended amount (XX CITATION). Our results show then that reserves designed in this fashion may struggle to provide perceived net benefits to many communities. In addition, even in the cases where NPB is highly positive, the time to achieve that NPB is quite long **should the timing be NB not NPBXX** (Fig.6). Therefore, even when benefits acrue there is still a period of losses that must be dealt with. For both of these reasons, we can consider the potential of our financial instruments. 

**10 year loans don't work well except for philanthropy**

```{r, fig.cap= 'Maximum % interest rate payable by a fishery for each species across a range of terminal reserve sizes'}
static__maxinterest_plot
```

The percent price increase required increased almost exponentially with the reserve size. However, the price increase shows the potential to offset much larger reserves, with increases of 20% capable of offsetting reserves closer to 30% in many cases. In addition, relatively small price increases (<20%) are sufficient to bring species such as blacknose shark and silver trevally, which were not benefited by design or loans, into a positive situation

* Price increases are good but not feasible for things like 50% reserves

```{r, fig.cap= ' % Price increase required by a fishery for each species across a range of terminal reserve sizes'}
static__priceinc_plot
```

## Optimal Impacts

We found the scenario *s* that maximized utility *U* (with an $\alpha$ of 0.5, signifying equal weighting between long and short-term benefits) for each species (Fig.1). 

* Even under optimal some species can't get positive NPB with this discount rate
* NPB takes longer than yield surplus
* Note that unlike Brown, shrinking is best if you have discounting and benefits are possible (growing is only best if you can't achieve benefits in the discounted window)
* The point of these is basically to say that we can replicateish results from Brown, and now we're going to build on them

```{r, fig.cap='NPB trajectories under optimal reserve scenario. Size of circle represents % of ares in reserve, color the yield surplus in a given year'}

opt_npb_plot

```

MPAs are commonly used as a tool for multi-species management, especially in the context simulated by this paper. As such, we should consider not only the effects of the the reserve on individual species but on the group of species. To address this we took the optimal reserve strategy for each species, and then applied it to each other species, to ask how far from the optimal NPB the other species' reserve strategy forced the target species NPB (Fig 2-3) 

* The basic point here is if you use a reserve designed for one species on another, how badly do you do? Need to do some tweaking here to get the color scales to come out right. 


```{r, fig.cap= 'Comparison of NPB performance for each species using the other species optimal reserve'}
species_comp_plot
```

# Discussion

* NPB matters: Even if there's a huge net benefit in the future, it doesn't matter if it takes 1000 years to get there
* As Brown et al. [-@Brown2014] showed, timing can be a problem with reserves
* The good news
    * For clades of species (snapper, emperor, grouper, parrot), you can get away with not having the exact right reserve, both individually and across species
    * reasonable price increases could offset the valley of death
    * Complications life slope and intercept help, but aren't deal breakers
* The bad news
    * Even a small discount rate quickly reducses the potential to achieve positive NPB: while there might be benefits to the long term planner good luck with the community. [@Teh2014] as evidence of high discount rate in artisanal fisheries. 
    * Some species aren't possible
    * 10 year Loans don't seem viable
    * Especially with a discount rate, the optimal or viable reserve size is quite a bit smaller than the target side touted by conservationists. 
* The take home
    * Design can certainly help, but it's somewhat finicky, and even done perfectly, might not then achieve the conservation objectives if the community has a strong discount rate
    * That leaves financial mechanisms. Which we show have some promise
    * We'll probbaly need RBFM to make them happen though
    
# Works Cited

