---
title: "Solutions for the Short-Term Economic Impacts of Marine Reserves"
author: "Dan Ovando, Dawn Dougherty, Jono Wilson"
date: "July 9, 2015"
output:
  html_document:
    fig_align: center
    fig_caption: yes
    fig_height: 6
    fig_width: 8
  pdf_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 8
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 8
number_sections: yes
csl: fish-and-fisheries.csl
bibliography: MPA Benefits.bib
toc: yes
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.path='Figs/', echo=FALSE, warning=FALSE, message=FALSE)
```
```{r}

ModelRun <- 'Full Grid 2.0'

load(paste('Results/',ModelRun,'/NutsPlots.Rdata',sep = ''))

```

# Abstract

Well-managed fisheries are critical for supporting healthy ocean ecosystems, coastal livelihoods, and food security for millions of people. Many communities lack the resources to implement effective fisheries management. No-take marine reserves are a relatively simple tool to conserve biodiversity and provide fishery benefits. Although empirical examples of fishery benefits from reserves are becoming more prevalent, the short-term economic impacts of establishing marine reserves are rarely considered.  In this paper we simulate fisheries for six species commonly caught in coastal fisheries in order to demonstrate the time required for a no-take reserve to provide a net improvement in the economic wellbeing of a fishing community. Our results show that while conservation benefits accrue rapidly, more than a decade is often required to provide net fisheries benefits, even under circumstances favorable for reserves. We explore a suite of strategies for mitigating these short-term economic losses, including flexible reserve designs, rights-based management, and loans. Our results indicate that combinations of these strategies can greatly reduce the short-term economic impacts of no-take marine reserves. Our findings provide mechanisms for improving the viability of no-take marine reserves as tools for fisheries management and conservation. 

# Introduction

* Plenty of papers have pointed out the challenges of using MPAs to manage fisheries
    * Conservation benefits clear
    * Fishery benefits are harder
* Nearly all papers focused on equilibrium though. This is a critical oversite, as practical management is often concerned both with long-term and short-term impacts
* Brown et al. [-@Brown2014] make an important contribution to this debate, and point out that it can take many years for MPAs to provide net economic benefits. They also show that MPAs can be designed to better achieve long or short-term objectives
* While Brown et al. [-@Brown2014] provide an important step in the discussion on the practical use of MPAs, there remain critical gaps in understanding how to best address the short-term economic impacts of MPAs. Speficifcally, they focus on optimized MPA size (though unoptimized trajectories, something to think about), and exclusively on design as a solution for MPA benefits. However, design can be challenging. Given the complex nature of marine ecosystems, the variety of species which MPAs are intended to simultaneously benefit, and the frequent scarcity of data around which to design reserves, it is highly unlikely that many communities will be able to design optimal reserves. 
* To that end, this paper addreses two important questions:
    1. How sensitive are the short-term economic impacts of reserves to imperfect design?
    2. How capable are design and financial solutions of offsetting short-term economic losses under imperfect design?
    
# Methods

## Operating Model

We analyzed 6 different species, intended to capture a range of life-history traits of species often targeted by developing country fisheries (see supplementary online material for species and life history parameters). Our model is single species, age-structured and assumed to be closed with respect to larval and adult emigration . The spatial configuration of the fishery includes 100 unique patches connected by larval and adult movement. The model tracks stock biomass, fishery yields, and net present benefits each year.  

The number of fish in patch i at age a at the beginning of year t+1 is

(1) $N_{i,a,t+1} = R_{i,t+1}$ if *a = 0*

(2) $N_{i,a,t+1} = N_{i,a-1,t}e^{-M-F_{i,t}\upsilon_{a-1}}$  if $1 \leq a < x$

(3) $N_{i,a,t+1} = N_{i,x-1,t}e^{-M-F_{i,t}\upsilon_{x-1}} + N_{i,x,t}e^{-M-F_{i,t}\upsilon_{x}}$  if $a = x$

where *R~i,t~*is the recruitment in patch *i* in year *t*, *F~i,t~* is the instantaneous fishing mortality in patch *i* in year *t*, $\upsilon_{a}$ is the selectivity of the fishing gear for a fish at age *a*,  *M* is the instantaneous natural mortality, and *x* is the maximum age recorded in the model (the plus group). This model assumes that the biological parameters of each species are homogeneous across space and time.

The simulations begin at an unfished equilibrium using a specified unfished initial recruitment in each patch *i*, *R~i,0~* such that

(4) $N_{i,a} = R_{i,0}$ if *a = 0*

(5) $N_{i,a} = N_{i,a-1}e^{-M}$  if $1 \leq a < x$

(6) $N_{i,a} = \frac{N_{i,x-1}e^{-M}}{1-e^{-M}}$  if $a = x$

The population is then fished down at a specified open access harvest rate in both patches to equilibrium conditions. We set this rate such that biomass over biomass at maximum sustainable yield (B/B~MSY~) is equal to 0.25 at equilibrium, representing an overfished fishery. We chose this level as the benefits of reserve formation were positively (and relatively linearly) related to the degree of overfishing. Starting at an overfished state then provides an optimistic estimation of the potential benefits of reserve formation.  

The average length (*l~a~*) of fish in each age class is calculated using a von Bertalanffy growth equation

(7) $l_{a} = L_{inf}(1-e^{-k(t-t_{0})})$

and then converted to average weight (*w~a~*) using:

(8) $w_{a}=b_{1}l_{a}^{b_{2}}$

We assume habitat quality to be the same in all patches.  Adult movement at each time step among the 100 patches is then calculated using a Gaussian dispersal kernel 

(9) $p_{i,j}=e^{\frac{-d_{i,j}^{2} }{2\sigma_{A}^{2}}}$

where *p~i,j~*  is the proportion of fish moving from area *i* to area *j*,  and *d~i,j~* is the distance between area *i* and area *j*. The model parameter $\sigma_{A}$ defines the movement range for the species. We wrap movement in order to remove edge effects. The relative proportions are then normalized so that the total proportion of fish moving from area *i* to any area sum to one. The number of fish in each age group one and older after movement are then

(10) $N_{i,a,t} = \sum^{100}_{j=1} N_{j,a,t}p_{i,j}$

To calculate recruitment each year, in each pach... **We use methods described in Babcock & MacCall [-@Babcock2011] XXX**

## Fishery Dynamics

The catch in each patch at each time step is calculated as

(11) $Y_{i,t} = \sum_{a}(N_{i,a,t}e^{-F_{i,t}\upsilon_{a}})$ 

We assume a closed population of fishers, where the number of fishers does not change with the implementation of a reserve (no emigration or immigration of boats), such that the effort from the reserve area is displaced to the fished area. This is intended to reflect a subsistence style fishery, with few alternative livelihoods besides fishing. Fishing effort is scaled by the relative commercial biomass,$\bar{B}_{i}$, in each patch where

(12) $\bar{B}_{i}= \frac{B_{i}}{\sum_{i}B_{i}}$

(13) $F_{i,t}=F_{pNTZ}(1+P_{NTZ})\bar{B}_{i}$

Where *F~pNTZ~* is the total possible instantaneous fishing pressure in the patch before the implementation of the reserve, and *P~NTZ~* is the fraction of patches that are in a reserve. 

## Reserve Implementation

We simulate a series of reserve implementation scenarios using the above operating model and fleet dynamics. A given scenario is defined by an terminal reserve size (% of area in a reserve), an "intercept" (% size of the terminal reserve in year 1), and a "slope" (% of run years at which the reserve reaches terminal size). In effect then we allow the final size, initial size, and rate at which the reserve reaches its final size to vary. We apply a subset grid of possible combinations of reserve size, intercept, and slope to each of the 6XX species included in this paper, providing an outline of the potential outcomes of reserve implementation. 

## Metrics

Throughout each scenario we keep track of live biomass of fish in the water and fishery yields over time. Net present balance (NPB) is our primary metric of performance, where NPB represents the cumulative yield benefits of a given reserve strategy relative to the status quo, calculated as

(14) $NPB_{s} = \sum^{T}_{t=0} \frac{Y_{s,t}-Y_{q}}{(1+r)^{t}}$

for any given species, where *t* is time, *Y* represents fishing yields, *s* is reserve implementation strategy, *q* is the status quo, *r* is the economic discount rate, and *T* is a specified number of years after reserve implementation in which *NPB* is calculated and compared across scenarios and species. We calculate the year at which NPB surpasses zero (increased benefits have compensated for short-term losses). NPB is an important output, since it reflects the net benefit that a community perceives from a given reserve strategy, relative to their benefit without the reserve. Alternatively, present balance (PB), the discounted difference between yields of a given reserve strategy and the status quo in year t, while important and a commonly presented metric, may not be as meaningful to a community (e.g. a 1 ton improvement over the status quo in year 10 of a reserve strategy may be of little value if 1,000 tons have been lost in years 1 through 9; see Fig.1 for an illustration of these concepts). 

We also analyze two potential financial mechanisms for offsetting short-term fishery losses stemming from the reserve; a loan system and a value added system. The total relative loss in yields experienced by the fishery for a given scenario *s* is 

(14) $O_{s} = -\sum^{T}_{t=0} min(0,\frac{Y_{s,t}-Y_{q}}{(1+r)^{t}})$

Where *O~a* is the amount of yield lost relative to the status quo. Under the loan strategy, a non-governmental organization, government, or private investor could provide a community with a loan to offset the initial losses from implementing a reserve, with a goal of being repaid by the future fishery benefits resulting from enhanced fishery productivity. The fishing community requests a loan totalling *O~a~*. The surplus available to pay the loan back over time are equal to 

(15) $S_{s} = -\sum^{T}_{t=0} max(0,\frac{Y_{s,t}-Y_{q}}{(1+r)^{t}})$
 
 Where *S~s~* is the total surplus in yields experienced by the fishery for a given scenario *s* over what the fishery would have experienced under the status quo. We then use the *optim* package in *R* [@RCoreTeam2015] to estimate the highest interest rate (%) that the community could afford in order to pay back a 10-year loan of magnitude *O_s~* using surplus *S~s~*. The higher the maximum potential interest rate, the more viable the loan is. 
 
For the value increase scenario, we implicitly assume a status quo value of $1 per unit weight (though this is an arbitraty choice that does not in fact matter). We then ask by what percent the value of the catch caught under a given scenario *s* would have to increase in order to completely offset *O~s~*. This is calculated as

(16) $P_{s} = 100(\sum_{t=0}^{T} \frac{Y_{q}}{Y_{q}+min(0,Y_{s,t}-Y_{q})}(1+r)^{-t}-1))$

Reserves often face competing obejctives between long-term and short-term benefits. This can be empirically illustrated by considering the net present benefits of the reserve over time with a discount rate *r* of 0 (long-term planner, $Y_{r_{0}}$) vs. the net present benefits of the reserve over time with a discount rate *r* > 0 (in this case we consider 0.1XX, $Y_{r_{0.1}}$)). In order to consider the relative utility of a given reserve strategy *s* we assign a weighting parameter $\alpha$ that can take any value from 0 to 1, such that total utillity *U* is calculated as

(17) $U_{s} = \alpha(\frac{Y_{r_{0},s}}{\sum_{s}Y_{r_{0},s}}) + (1-\alpha)(\frac{Y_{r_{0.1},s}}{\sum_{s}Y_{r_{0.1},s}})$

This allows us to calculate utility focused solely on long-term benefits ($\alpha$=1), short-term benefits ($\alpha$=0), or any relative weighting in between. 

# Results

## Optimal Impacts

We found the scenario *s* that maximized utility *U* (with an $\alpha$ of 0.5, signifying equal weighting between long and short-term benefits) for each species (Fig.1). 

* Even under optimal some species can't get positive NPB with this discount rate
* NPB takes longer than yield surplus
* Note that unlike Brown, shrinking is best if you have discounting and benefits are possible (growing is only best if you can't achieve benefits in the discounted window)
* The point of these is basically to say that we can replicateish results from Brown, and now we're going to build on them

```{r, fig.cap='NPB trajectories under optimal reserve scenario. Size of circle represents % of ares in reserve, color the yield surplus in a given year'}

opt_npb_plot

```

MPAs are commonly used as a tool for multi-species management, especially in the context simulated by this paper. As such, we should consider not only the effects of the the reserve on individual species but on the group of species. To address this we took the optimal reserve strategy for each species, and then applied it to each other species, to ask how far from the optimal NPB the other species' reserve strategy forced the target species NPB (Fig 2-3) 

* The basic point here is if you use a reserve designed for one species on another, how badly do you do? Need to do some tweaking here to get the color scales to come out right. 


```{r, fig.cap= 'Comparison of NPB performance for each species using the other species optimal reserve'}
species_comp_plot
```

```{r, fig.cap= 'Comparison of NPB performance for each species using the other species optimal reserve (outliers out)'}
species_compnoshark_plot
```

Rather than comparing the performance of individually optimized runs, we can also ask how the economic impacts of reserves evolve when a common reserve strategy is implemented across all species. We selected the reserve strategy (the unique combination of terminal size, intercept, and slope) that maximized the net utility across all six species. 

* Net resut, solid results for some species, at the expense of sharks and trevally

```{r, fig.cap= 'Comparison of NPB performance across each species using the across-species optimal reserve strategy'}
unified_npb_plot
```

## Impacts of Wrong Size Reserve

Results up to here show that yes reserves can take time to provide benefits if at all, design can help a bit, multi-species adds another layer though many species do just about as well with similar species reserves as they do with their optimal one. 

We first consider how sensitive our results are to implementing the incorrect terminal reserve size. Or in other words, we consider our results under a range of terminal reserve sizes, and ask how sensitive our results are to being in a particular window. If it's small, unlikely that we'll find it in the real world.  

* For bumphead, grouper, and snapper peak NPB occurs at around 10% reserve size, neagative by about 20%. Emperor much larger. Blacknose shark and trevally not possible. This suggests that reserves less than 20% viable from an NPB perspective for many common species, not so much beyond that. But, it's not knife edged (optimal or bust)

```{r, fig.cap= 'NPB under possible terminal reserve sizes for each species'}
static_NPB_plot
```

So, under static scenario we see that NPB is somewhat sensitive to terminal reserve size, but not extremely; for a general class of reserves under 20% seems possible, though the scale of it matters. What about other metrics?

* We see that even though positive NPB is possible up to the sizes seen in Fig.4, it takes a long time to achieve. So, while the ability to break even at all is somewhat insensitive to reserve size, the amount of time required increases almost exponentially in reserve size.

```{r,fig.cap= 'Number of years to achieve positive NPB.'}

static_netbenefit_plot

```

Given then that we've still got a valley of death to deal with, how do the loan and price increase scenarios perform under potential uncertainty in the correct reserve to apply. 

```{r, fig.cap= 'Maximum % interest rate payable by a fishery for each species across a range of terminal reserve sizes'}
static__maxinterest_plot
```

```{r, fig.cap= ' % Price increase required by a fishery for each species across a range of terminal reserve sizes'}
static__priceinc_plot
```

## Impacts of Wrong Implementation strategy

Lastly, let's look at what happens when we consider both terminal reserve size and intercept (shrinking or growing). Since 3d plots are bad we fix the slope at 10 years, meaning that the reserve hits terminal size in 10 years. 

```{r, fig.cap= ' NPB as a function of terminal reserve and intercept'}
npb_surface_plot
```

```{r, fig.cap= ' % Price increase required as a function of terminal reserve and intercept'}
priceinc_surface_plot
```


```{r, fig.cap= ' Viable loan type as a function of terminal reserve and intercept'}
loantype_surface_plot
```
