---
title: "Solutions to the Short-Term Economic Impacts of Marine Reserves"
author: "Dan Ovando, Dawn Dougherty, Jono Wilson"
date: "July 9, 2015"
output:
  word_document:
    fig_caption: yes
    fig_height: 4
    fig_width: 6
  pdf_document:
    fig_caption: yes
    fig_height: 5
    fig_width: 6
  html_document:
    fig_align: center
    fig_caption: yes
    fig_height: 6
    fig_width: 8
header-includes:
- \usepackage{setspace}
- \doublespacing
- \usepackage{lineno}
- \linenumbers
number_sections: yes
csl: fish-and-fisheries.csl
bibliography: MPA Benefits.bib
toc: yes
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.path='Figs/', echo=FALSE, warning=FALSE, message=FALSE)
```
```{r}
library(gridExtra)
library(ggplot2)
library(dplyr)
library(tidyr)
library(knitr)
ModelRun <- 'Full Grid 2.2 BvBmsy _15'

load(paste('Results/',ModelRun,'/NutsPlots.Rdata',sep = ''))

#####Example Shrinking NUTZ concept

CartoonPlot<- function(Theme)
{

r=0.24
K=100
Nvec=NA
Nvec[1]=K
u1=0.16
u2=0.12
yvec=NA

for(t in 2:150){
  if(t<100)u=u1 else u=u2
  Nvec[t]=Nvec[t-1]+r*Nvec[t-1]*(1-Nvec[t-1]/K)-u*Nvec[t-1]
  yvec[t-1]=u*Nvec[t-1]

  }



Years=1:149
Nvec=Nvec[1:149]
Yield=(yvec-yvec[98])/max(yvec)                 #creat standardized deviations from status quo
Biomass=(Nvec-Nvec[98])/max(Nvec)
dat=data.frame(Years,Biomass,Yield)

datA=subset(dat,Years>90 & Years<=149)
 datA$Years=-7:51
 
 datA$Balance=cumsum(datA$Yield)

#find year balance is positive for shaded area cutoff
test=subset(datA,Years>0)
test$flag=0
test$flag[test$Balance>0]=1
test$dup=duplicated(test$flag)
breakeven=which(test$dup==FALSE)[2]
breakYear=test$Years[breakeven]

#long format
longdat <- reshape(datA[,1:3], 
  varying = c("Biomass","Yield"), 
  v.names = "value",
  timevar = "Objectives", 
  times = c("Biomass","Yield"), 
  direction = "long")

 


p <- ggplot(longdat, aes(x=Years,y=value))

p + geom_area(data=subset(longdat,Years<=12 & Objectives=="Yield"),  fill="darkorange")+ geom_area(data=subset(longdat,Years>=12 &Years<=breakYear& Objectives=="Yield"),  fill="cornflowerblue")+ geom_line(aes(colour=Objectives),size=1.1)+ geom_vline(xintercept = 30,linetype=2) + scale_color_manual(values=c("aquamarine3", "black"))  + ylab("Deviation from Status Quo")  + scale_x_discrete(breaks=c(0,30),labels=c("0","Yield Balance"))     + scale_y_continuous(limits=c(-0.1, 0.2),breaks=0) + Theme
}


```

# Cover Letter

Dear Editor, 

The extensive debate on when and if no-take marine reserves can benefit fisheries has centered around long-term economic effects. Very little work has considered the economic impacts of reserves over time frames that matter more to communities and decision makers. Our paper, *Solutions to the Short-Term Economic Impacts of Marine Reserves", builds from the existing literature on marine reserves to advance our understanding of how reserves affect fisheries over time, and to what extent design and financial instruments can offset economic losses. 

We find that a decade or much more is often needed for a community to see a net benefit from implementing a marine reserve, even if that eventual benefits are very large. Careful design of the reserve can help offset early losses, but financial strategies such as improving the value of the catch show much more promise. Together our results provide a novel consideration of the ways in which reserves affect fishing communities over the short-term, and show that economic tools may be the future for resolving those losses. 

Our paper suggests a framework for assessing and communicating the economic effects of no-take marine reserves on fisheries. The case studies included provide a "best-case scenario" against which to assess the likely fishery impacts of reserves in other locations. Marine reserves can have substantial benefits to conservation and fisheries, but overlooking the short-term economic impacts is both misleading to fishing communities and detrimental to conservation in the long-run. Our goal is for this paper to shift the discussion of marine reserves as fishery management tools towards the challenges and solutions for the short-term economic impacts. Given its integration and advancement on a broad literature, novel findings, and wide scope, we feel that this paper is an ideal candidate for publication in *Fish and Fisheries*. 

Thank you for your consideration, 

Dan Ovando


# Abstract

Well-managed fisheries are critical for supporting healthy ocean ecosystems, coastal livelihoods, and food security for millions of people. Many communities lack the resources to implement effective fisheries management. No-take marine reserves are a relatively simple tool to conserve biodiversity and provide fishery benefits. While the biological and long-term economic effects of reserves on fisheries have been well studied, the short-term economic impacts of establishing marine reserves are rarely considered.  In this paper we simulate fisheries for six species commonly caught in coastal fisheries in order to demonstrate the time required for a no-take reserve to provide a net improvement in the economic well-being of a fishing community. Our results show that while conservation benefits accrue rapidly, more than a decade is often required to provide net fisheries benefits, even under circumstances favorable for reserves. We explore a suite of strategies for mitigating these short-term economic losses, including flexible reserve designs, loans, and value increases. Our results indicate that reserves may struggle to provide short-term economic benefits to artisnal fisheries, and value increases show the most potential for offsetting these losses. Our findings provide mechanisms for improving the communication and use of no-take marine reserves as tools for fisheries management and conservation. 

# Introduction

More than 260 million people across the globe earn their livelihood in fishing related industries [@Teh2014]. Fish is a primary source of protein to over one billion people [@FAO2011]. Yet the sustainability of the fishing industry and the potential for wild capture fisheries to feed a growing population is dependent on the implementation and enforcement of effective systems of governance and management. No-take marine reserves (hereafter reserves), areas set off-limits to fishing, are a widely used tool for protecting fish populations and are known to provide key conservation benefits that can improve ecosystem services to coastal environments. Conservation benefits of marine reserves include the maintenance of spatial population structure of fish stocks [@Berkeley2004; @White2008; @Rassweiler2012], protection of essential fish habitat, increased species diversity and fish biomass [@Lester2009], a hedge against changes in environmental conditions [@Stefansson2005; @Costello2008], an effective means of protecting spatially complex marine populations [@White2008; @Rassweiler2012], and can serve as reference areas to set local management regulations and disentangle the effects of fishing from environmental variability [@Wilson2013]. Enhanced biological production inside reserves can benefit adjacent fisheries through adult spillover [@Roberts1991; @Allison1998; @McClanahan2008] and larval export [@Cudney-Bueno2009; @Pelc2010], especially in situations where the size of the reserve is larger than the adult home range size, and smaller than the scale of larval dispersal [@Gerber2003]. 

In some cases marine reserves can serve as a mechanism for simultaneously achieving conservation outcomes and improving the productivity of fisheries [@Gaines2010; @Hilborn2006]. The case for using reserves for both conservation and fishery management is often made in the context of developing world fisheries, which may have little capacity to perform more complex fishery management practices (such as quotas, size limits, or effort restrictions) [@Holland1996]. In fact, reserves have a long history as fishery management tools in many island nations [@Johannes1978; @Johannes2002]. However, the ability of marine reserves to provide fishery benefits is dependent on a suite of factors, including the size of reserve relative to the home range size of the species, the dispersal potential, geographic extent of the stock, as well as the status of the fishery prior to implementation of reserves [@Sanchirico2001; @Costello2008; @White2008; @Rassweiler2012; @Sanchirico2006; @Smith2003]. Moreover, the implementation of marine reserves necessarily reduces the spatial extent of the fishery, often limiting take in prime fishing grounds and concentrating effort into areas where fishing is still allowed [@Halpern2004]. 

The potential and challenges of utilizing reserves as fishery management tools have been well studied [@Hilborn2004], though it is worth noting that the vast majority of this work is simulation based, and little causal empirical evidence of the fishery impacts of reserves is available [see @Fletcher2014, and @Sala2013 and references therein for examples of the effects of reserves on fisheries]. However, there is a critical gap in the understanding how the economic effects of reserves on fisheries play out over time. Nearly all of the published research on the topic has considered the long-term (or equilibrium) economic impacts of implementing a marine reserve (note that for this paper, the we refer solely to fishing when we consider economic impacts). 

While the long-term impacts are critical to understanding the interactions between reserves and fisheries, from the perspective of fishing communities the short-term impacts may be of much greater consequence. Depending on the time horizon that a community is able or willing to consider, a reserve that provides long-term fishery benefits may provide no practical benefit to today's fishers and decision makers. Alternatively, even in conditions in which a community perceives long-term benefits stemming from a reserve, they may have to endure years of reduced fishing income and food until those benefits arrive.These short-term consequences of reserves can have profound implications on the financial health and food security of fishing communities, affecting local support and buy in for enforcement policies, trust in management and supporting organizations, and ultimately the sustainability of the fishery itself. 

Brown et al. [-@Brown2014] provides an important contribution to our understanding of the short-term impacts of marine reserves. They illustrate that there are often tradeoffs between short-term and long-term economic fishing benefits from reserves, and that alternative strategies for designing those reserves (how large they are and how that size changes over time) can affect the short-term economic effects of a reserve. Brown et al. [-@Brown2014] launches an important discussion on the ways in which we might choose to design reserves in order to provide fishery benefits, and the ways in which the consequences of those choices can be communicated to fishing communities. In particular, they point out that reserves designed around long-term benefits have substantial short-term costs. Our paper builds on this work by focusing on potential solutions to the trade-offs identified by Brown et al. [-@Brown2014]. 

One potential strategy for minimizing economic impacts, building off of Brown et al. [-@Brown2014], is to optimize the implementation of a reserve in order to maximize a community's benefit. For example, perhaps the short-term economic impacts of a reserve can be minimized by finding the right reserve size, or trajectory of reserve sizes. This consideration of the optimal design of reserves has been the focus of most of the literature on reserves as fishery management tools. Alternatively, what if we shift our focus from designing reserves to prevent fishing losses, to offsetting losses that do occur? This may be ideal due to the difficulty in designing "optimal" reserves in the real world, where data and capacity are often limited. 

We consider two financial strategies to offset reserve-induced economic losses: loans and value increases. Under the loan scenario, we consider the ability of a community take out a loan to cover short-term economic losses, and pay back that loan uses future fishery benefits provided by the reserve. This loan could be provided by a commercial entity, an NGO, or a philanthropy for example. Under the value increase scenario, we ask how much the price the community receives for their catch would have to increase to offset short-term economic losses caused by a reserve. Increases in value could be achieved by improving the quality of the catch (e.g. providing an ice plant), providing access to more lucrative markets (e.g. seafood distributors committed to sourcing sustainably), or reducing costs (e.g. through coordinated fishing efforts).

We analyze the potential of design and financial instruments to offset economic losses by using a simulated developing world fishery targeting a variety of typical tropical reef species. We focus on artisanal fisheries such as these, since small-scale fisheries throughout the developing tropics are often considered as sites for reserve based management, due to the limited capacity for more involved fishery management practices. We find that reserves may struggle to provide net fishing benefits at a time scale that is of value to fishing communities for many common reef associated fish species, and financial mechanisms may be needed to offset these losses.

# Methods

## Operating Model

We analyzed 6 different species, representing a range of life-history traits of species often targeted by tropical developing country fisheries. Our model is single species, age-structured, and is closed to larval and adult emigration and immigration. The spatial configuration of the fishery includes 100 unique patches with wrapped edges connected by larval and adult movement. The model tracks stock numbers, biomass, and fishery yields over time. This structure best represents a small-scale fishing community on an island or isolated stretch of coastline. 
Life history values were drawn from stock assessments where possible, in order to help ensure reliable and consistent values (Table.1). The recruitment model (or the functional form of the density dependence relationship) was selected from the possible structures outlined in Babcock & MacCall [-@Babcock2011] using expert judgement.  The *Range* parameter scales the number of patches moved by adults in a time step, with 100% indicating total mixing and 0% a completely sedentary species. 

```{r}

LifeHistories <- read.csv('Inputs/Life History Inputs.csv',stringsAsFactors = F)

LifeVars <- c('CommName','Range','m','k','Linf','t0','AgeMa50','LengthMa50','BH.Steepness','DDForm','Source')

LifeTable <- LifeHistories[, LifeVars] %>%
  rename(Species = CommName, h = BH.Steepness)


LifeTable$DDForm[LifeTable$DDForm == 'Babcock1'] <- 'I'

LifeTable$DDForm[LifeTable$DDForm == 'Babcock2'] <- 'II'

LifeTable$DDForm[LifeTable$DDForm == 'Babcock3'] <- 'III'

LifeTable$DDForm[LifeTable$DDForm == 'Babcock4'] <- 'IV'

LifeTable$DDForm[LifeTable$DDForm == 'Babcock5'] <- 'V'

LifeTable$DDForm[LifeTable$DDForm == 'Shark'] <- 'I'

LifeTable$DDForm <- paste(LifeTable$DDForm, '*',sep = '')

LifeTable <- LifeTable %>% 
  rename('Recruitment Model' = DDForm)

LifeTable$Range <- paste(100*LifeTable$Range, '%',sep = '')

LifeTable$Range <- paste(LifeTable$Range, '*',sep = '')

kable(LifeTable, digits = 2, caption = 'Life history values used. m is natural mortality, Linf, k, and t0 are the Von Bertalanffy growth parameters, Age/Length Ma50 are the respective age or length at which the 50% of the individuals have reached sexual maturity, h is steepness, and the roman numeral under "Density Dependence" corresponds with the density dependence form from Babcock & MacCall 2011 that was used. Values with * were assumed')

```

The number of fish in patch i at age a at the beginning of year t+1 is

(1) $N_{i,a,t+1} = R_{i,t+1}$ if *a = 0*

(2) $N_{i,a,t+1} = N_{i,a-1,t}e^{-M-F_{i,t}\upsilon_{a-1}}$  if $1 \leq a < x$

(3) $N_{i,a,t+1} = N_{i,x-1,t}e^{-M-F_{i,t}\upsilon_{x-1}} + N_{i,x,t}e^{-M-F_{i,t}\upsilon_{x}}$  if $a = x$

where *R~i,t~*is the recruitment in patch *i* in year *t*, *F~i,t~* is the instantaneous fishing mortality in patch *i* in year *t*, $\upsilon_{a}$ is the selectivity of the fishing gear for a fish at age *a* (which we assume to be 1 for all ages),  *M* is the instantaneous natural mortality, and *x* is the maximum age recorded in the model (the plus group). This model assumes that the biological parameters of each species are homogeneous across space and time.

The simulations begin at an unfished equilibrium using a specified unfished initial recruitment in each patch *i*, *R~i,0~* such that

(4) $N_{i,a} = R_{i,0}$ if *a = 0*

(5) $N_{i,a} = N_{i,a-1}e^{-M}$  if $1 \leq a < x$

(6) $N_{i,a} = \frac{N_{i,x-1}e^{-M}}{1-e^{-M}}$  if $a = x$

The population is then fished down at a specified open access harvest rate in both patches to equilibrium conditions. We set this rate such that biomass relative to biomass at maximum sustainable yield (B/B~MSY~) is equal to 0.15 at equilibrium. We chose this level to simulate a highly overfished fishery with little to no capacity for management, and to ensure that the reserve had high potential to benefit the fishery in the long-term. Starting from this overfished state provides an optimistic estimation of the potential benefits of reserve formation.  

The average length (*l~a~*) of fish in each age class is calculated using a von Bertalanffy growth equation

(7) $l_{a} = L_{inf}(1-e^{-k(t-t_{0})})$

and then converted to average weight (*w~a~*) using:

(8) $w_{a}=b_{1}l_{a}^{b_{2}}$

We assume habitat quality to be the same in all patches.  Adult movement at each time step among the 100 patches is then calculated using a Gaussian dispersal kernel 

(9) $p_{i,j}=e^{\frac{-d_{i,j}^{2} }{2\sigma_{A}^{2}}}$

where *p~i,j~*  is the proportion of fish moving from area *i* to area *j*,  and *d~i,j~* is the distance between area *i* and area *j*. The model parameter $\sigma_{A}$ defines the movement range for the species, and is scaled by the *Range* parameter. We wrap movement in order to remove edge effects. The relative proportions are then normalized so that the total proportion of fish moving from area *i* to any area sum to one. The number of fish in each age group one and older after movement are then

(10) $N_{i,a,t} = \sum^{100}_{j=1} N_{j,a,t}p_{i,j}$

To calculate recruitment each year in each patch we use the recruitment models described in Babcock & MacCall [-@Babcock2011], in order to allow the nature of density dependence to vary among species (for example, pre or post settlement density dependence). 

## Fishery Dynamics

The catch in each patch at each time step is calculated as

(11) $Y_{i,t} = \sum_{a}(N_{i,a,t}e^{-F_{i,t}\upsilon_{a}})$ 

We assume a closed population of fishers, where the number of fishers does not change with the implementation of a reserve (no emigration or immigration of boats), such that the effort from the reserve area is displaced to the fished area. This is intended to reflect a subsistence style fishery, with few alternative livelihoods besides fishing. We do not however explicitly model fishers or vessels, but rather fishing mortality *F*, in order to reduce model components. Fishing mortality is scaled by the relative commercial biomass,$\bar{B}_{i}$, in each patch where

(12) $\bar{B}_{i}= \frac{B_{i}}{\sum_{i}B_{i}}$

(13) $F_{i,t}=F_{i,pNTZ}(1+P_{NTZ})\bar{B}_{i,t}$

Where *F~pNTZ~* is the total possible instantaneous fishing pressure in the patch *i* before the implementation of the reserve, and *P~NTZ~* is the fraction of patches that are in a reserve. 

## Reserve Implementation

We simulate a series of reserve implementation scenarios using the above operating model and fleet dynamics. A given scenario is defined by an terminal reserve size (% of area in a reserve), initial size (% of the area in a reserve in year 1), and a "slope" (% of run years at which the reserve reaches terminal size). In effect then we allow the final size, initial size, and rate at which the reserve reaches its final size to vary. We apply a fine-scale grid of factorial combinations of final reserve size, initial reserve size, and slope to each of the 6 species included in this paper, providing an outline of the potential outcomes of reserve implementation. Reserves are applied as a continuous block in the center of the system (alternative configurations such as a reserve on the left or right side of the system do not alter results). 

Reserves often face competing objectives between long-term conservation benefits and short-term economic benefits. This can be empirically illustrated by considering the cumulative biomass of fish in the water over time with a discount rate *r* of 0 (long-term conservation planner, $B_{r_{0}}$) vs. the net present benefits of the reserve over time with a discount rate *r* > 0 (in this case we consider 0.2, $Y_{r_{0.2}}$)). In order to consider the relative utility of a given reserve strategy *s* we assign a weighting parameter $\alpha$ that can take any value from 0 to 1, such that total utility *U* is calculated as

(19) $U_{s} = \alpha(\frac{Y_{r_{0.2},s}}{\sum_{s}Y_{r_{0.2},s}}) + (1-\alpha)(\frac{B_{r_{0},s}}{\sum_{s}B_{r_{0},s}})$

This allows us to calculate utility focused solely on discounted fishery benefits ($\alpha$=1), long-term conservation benefits ($\alpha$=0), or any relative weighting in between). "Optimal" reserve policies are found by determining the combination of terminal reserve size, initial reserve size, and slope that maximizes utility *U*. 

For the majority of scenarios, we consider a single-species fishery, and apply reserve strategies independently for each species. In reality many artisanal fisheries are likely to target multiple species at once. To account for this, we consider the economic impacts of a reserve scenario designed around one species but applied to all six of the fish considered here. For each of the six species included here, we find the utility maximizing reserve strategy. We then apply that optimal strategy to each of the other species' fishery, and asses how detrimental to utility that strategy is when applied to species for which it was not designed. 

## Measuring Economic Impact

Throughout each scenario we keep track of live biomass of fish in the water and fishery yields over time. Net present balance (NPB) is our primary metric of performance, where NPB represents the present value of the cumulative yield benefits of a given reserve strategy relative to the status quo, calculated as

(14) $NPB_{s} = \sum^{T}_{t=0} \frac{Y_{s,t}-Y_{q}}{(1+r)^{t}}$

for any given species, where *t* is time, *Y* represents fishing yields, *s* is reserve implementation strategy, *q* is the status quo, *r* is the economic discount rate, and *T* is a specified number of years after reserve implementation in which *NPB* is calculated and compared across scenarios and species. We calculate the year at which NPB surpasses zero (increased benefits have compensated for short-term losses). NPB is an important output, since it reflects the benefits that a community today perceives they will receive over time from a given reserve strategy, relative to the benefits they would have received without the reserve. So a positive NPB implies that the community perceives a net improvement in catches resulting from the reserve, a negative a net loss in catches over time resulting from the reserve. Alternatively, the yield balance, the difference between catches with and without a given reserve in year *t*, while important and a commonly presented metric, may not be as meaningful to a community. For example, a one ton increase in catches, relative to the status quo, that takes ten years to develop is of little value if 1,000 tons have been lost in years 1 through 9. 

To illustrate this concept, consider an overfished fishery at equilibrium, such as the one simulated here. In year 1, we implement a marine reserve of an arbitrary size (Fig.1). Total biomass in the system begins to increase monotonically over time, a commonly reported outcome of marine reserves. However, the yield or economic benefits are less often considered. Catches decline immediately once the reserve is put in place, due to the loss of fishing grounds.  Yields then gradually increases as  biomass in the reserve builds and larvae and adults spill to fished areas, until eventually catches in a given year start to exceed the amount of fish caught by the community before the reserve (Fig.1). While the community in that year is catching as many fish as they were before the reserve, the community has still lost a substantial amount of catch in the years leading up to that point (the red area, Fig.1). It may take several more years of benefits for the increases in catches resulting from the reserve (the blue area, Fig.1) to offset the early losses (the dashed vertical line, Fig.1). By focusing on NPB then, this study examines the ability of reserves to provide a net perceived benefit to a community today. 

```{r, fig.cap= 'Illustration of the trajectory of yield and biomass benefits following a reserve. A reserve is implemented in year 1. Black line represents fishing yields relative to the status quo pre reserve, the blue line biomass. The red area is the total losses in yields, the blue area the total gains. The vertical grey dashed line shows the year in which the NPB becomes >=0; when the blue area is equal to the red area'}

Cartoon <- CartoonPlot(SimpleTheme)
Cartoon
```

NPB is a function of both the stream of future yields relative to the status quo and the discount rate. A discount rate of 0.05 is the default value in much of the economic literature. However, our thought experiment for this study is the management of an artisnal fishery. While few studies have actually estimated the discount rate for artisanal fishers, those that have report much higher discount rates than 0.05. Johnson & Saunders [-@Johnson2014] and Curtis [-@Curtis2002] found discount rates of artisnal fishermen of ~0.22 (mean) and ~ 0.35 (median), respectively, meaning that the fishermen in those studies value profits today much more than profits tomorrow. We chose a discount rate value of 0.2 as our default, reflective of Johnson & Saunders [-@Johnson2014], in order to reflect the higher discount rate of an artisanal fishery, while still allowing some preference for future benefits by the community.

## Financial Mechanisms

We also analyze two potential financial mechanisms for offsetting short-term fishery losses stemming from the reserve; a loan system and a value added system. The total relative loss in yields experienced by the fishery for a given scenario *s* is 

(15) $O_{s} = -\sum^{T}_{t=0} min(0,Y_{s,t}-Y_{q})$

Where *O~s~* is the amount of yield lost relative to the status quo (*sq*) over time period *T*. Under the loan strategy, a non-governmental organization, government, or private investor could provide a community with a loan to offset any initial losses from implementing a reserve, with a goal of being repaid by the future fishery benefits resulting from enhanced fishery productivity. The fishing community requests a loan totaling *O~s~*. The surplus available to pay the loan back over time *T* are equal to 

(16) $S_{s} = -\sum^{T}_{t=0} max(0,Y_{s,t}-Y_{q})$

Where *S~s~* is the total positive difference in yields (if any) for a given reserve scenario *s*,over what the fishery would have experienced under the status quo.

For a given loan interest rate *i* for a loan of duration *T*, the total loan payments are equal to 

(17) $C = Tp( \frac{\frac{i}{p}{O}}{1-(1+i)^{-Tp}})$

where *p* is the number of payments per year. Setting the time window of the loan to *T* of 10 years with *p* of 4 payments per year, we then use the *optim* package in *R* [@RCoreTeam2015] to estimate the highest interest rate *i* (%) that the community could afford in order to pay back a 10-year loan such that *C~s,i~ <= S~s~*; meaning that the total loan payments must be less than or equal to the surplus generated by the reserve. The higher the maximum potential interest rate, the more viable the loan is. We break loans apart in to three categories: Interest rates greater than 15% are considered "commercial" (the high rate reflective of the risk in fisheries loans), 5%-15% "social investment" loans, provided by entities that expect a rate of return but may be less concerned with turning a profit, and philanthropy (<5%). 
 
For the value increase scenario, we implicitly assume a status quo value of $1 per unit weight (though this is an arbitrary choice that does not influence the results). We then ask by what percent the value of the catch caught under a given scenario *s* would have to increase in order to completely offset the greatest loss of yields seen across all years

(18) $P_{s} = 100(\frac{Y_{q}}{Y_{q}+min(Y_{s}-Y_{q})}-1))$


# Results

We first provide an illustration of the importance of the assigned discount rate *r*, using the yellowtail snapper fishery (Fig.XX). The discount rate reflects the degree to which money today is favored over money tomorrow; the higher the rate, the less a community (or individual) values something in the future relative to today. For a given discount rate, we find the reserve scenario *s* (combination of terminal size, starting size, and slope) that maximizes the community's utility per Eq.19 (using $\alpha = 0$). With a discount rate of 0 the NPB is simply the cumulative sum of the yield balances over time. Under this scenario, the optimal policy for the yellowtail snapper fishery is to put a substantial portion of the fishery into a reserve for nearly a decade, reducing the reserve size once the fishery begins to recover, resulting in substantial economic gains for the fishery by year 50. 

Under the 0.05 discount rate scenario, the optimal reserve scenario from the perspective of a community designing a reserve today would be to implement a reserve covering ~50% of the fishery, and then reduce it's size more quickly than under the *r*=0 scenario. This strategy results in a positive NPB for the community in slightly over 10 years, meaning that from the community's perspective, they would need to feel confident that they will be there and fishing for at least 10 years in order for a reserve based around yellowtail snapper to be worthwhile for them to implement today. Under the 0.2 discount rate scenario for this yellowtail snapper fishery, the NPB maximizing strategy is still to shrink the reserve over time, but the reserve size starts at only ~25%, and shrinks to almost nothing (Fig.XX). With a discount rate of 0.2 only marginal gains in NPB are possible. Under this yellowtail snapper example then, the benefits a community perceives they will receive from a reserve are highly dependent on the extent to which a community is able to forgo current catches for future benefits, as reflected by the discount rate.


```{r, fig.cap='Example NPB trajectories under optimal reserve scenario under different discount rates for yellowtail snapper'}

discount_rate_plot

```

## Design Solutions to Short-Term Losses

For the remainder of this experiment we consider a discount rate of 0.2. How big a reserve should be is a fundamental question when using marine reserves as fishery management tools. With this discount rate of 0.2 in mind, how does the final size of the reserve affect a community's NPB? Under this thought experiment, the community picks one reserve size, ranging from 2.5% to 50% of the available habitat, and immediately implements it. We apply this procedure to each of the 6 species evaluated here, running over a 50 year time horizon. 

Due to the overfished conditions simulated, any of the reserve sizes tested here provide at least equal to or greater lifetime catches than those that would have occurred without the reserve (Fig.XX). However, it is much more difficult for a reserve to provide positive NPB values to the simulated fisheries. Our results show that with a discount rate of 0.2, only the red throat emperor and yellowtail snapper fisheries are capable of providing substantially positive NPB values to the community under any of the evaluated reserve sizes, though at small reserve sizes red grouper and bumphead parrotfish fisheries were able to achieve NPBs of near to or slightly above 0 (Fig.XX). The red throat emperor fishery is the most promising; reserves covering less than 35% of the fishery all provide positive NPB to the fishery within 10 years, with peak benefits occurring at 15% reserve coverage. Positive NPB is possible for the yellowtail snapper fishery, but only for reserves covering less than 5% of the fishery. The time to achieve positive NPB for the yellowtail snapper is longer, generally 15 years if positive NPB values are possible. The red grouper and bumphead parrotfish fisheries received positive NPB from very small reserves only, with net benefits arriving in 20 or more years, while reserves were unable to provide positive NPB for the blacknose shark and silver trevally fisheries under any reserve size (Fig.XX).

```{r, fig.cap= 'NPB with discount rate of 0.2, across a range of possible reserve sizes for each fishery. Color represents the change cumulative in yields over the yields that would have occured without the reserve. Size of circles represents the number of years until NPB is greater than or equal to 0'}
static_NPB_plot
```

Brown et al. [-@Brown2014] suggest that one solution to offsetting short-term fishery losses seen when a static reserve size is implemented may be to allow the reserve size to change over time. We consider the potential NPB outcomes for our simulated community from allowing the reserve to grow or shrink with time. We set $\alpha$ to 0.9, meaning that 90% of the community's utility comes from fishery benefits, but some consideration is made for long-term conservation outcomes (this is done to ensure that a reserve of any size is optimal in the future).

Our results show that dynamic designs can improve the economic outcomes of the reserve in all fisheries except those for blacknose shark and silver trevally. Under the optimal strategy, yields generally began to exceed status quo yields within 5-10 years. The time to positive NPB was much longer, generally 10 or more years when positive NPB values were possible. In contrast to Brown et al. [-@Brown2014], which suggested a growing reserve as a solution to short-term economic losses, we find that the optimal strategy for a reserve that is capable of any positive NPB is to start at a larger reserve size and decrease in size over time (Fig.XX). 

```{r, fig.cap='NPB trajectories under optimal reserve scenario. Size of circle represents % of ares in reserve, color the yield surplus in a given year'}

opt_npb_plot

```

We find that the utility outcomes for a given species' fishery are relatively insensitive to application of another species' fishery's optimal reserve policy. For example, using a reserve designed around yellowtail snapper to manage blacknose shark only reduces the utility of the blacknose shark fishery by ~5%, relative to the highest utility that the blacknose shark fishery could achieve (Fig.XX). The red throat emperor designed reserve (terminal size of 15%) is the most robust of the possible scenarios, with respect to utility, when applied to all the other fisheries in the study. 

```{r, fig.cap= 'Comparison of NPB performance for each species using the other species optimal reserve'}
species_comp_plot
```


## Financial Solutions to Short-Term Losses

Turning from design solutions, we now consider the plausibility of loans and value increases to offset reserve-induced fishery losses. For this experiment, we once again consider a single reserve size applied at once. For the loan, community's goal would be to pay back that loan using the eventual yield increases from the reserve over a ten year period with four payments per year. It is important to note that this analysis considers whether the community could feasibly pay back a loan at a given rate, not whether the loan would be acceptable given their discount rate. 

We find that under these assumptions, loans are not a broadly viable strategy for offsetting the short-term economic losses of the reserve. Loans at any rates above philanthropic levels are viable only for red throat emperor, yellowtail snapper, and red grouper fisheries. In the case of red throat emperor fishery, the community could afford to pay back a loan at very high interest rates, up to and above 25%,if the reserves is less than 25% of the area. Under these rates the community could possibly afford to take a loan out from a commercial bank to pay for the short-term yield losses of the reserve. Social investment loans (interest rates >5% and less than 15%) might be viable for red throat emperor fishery with reserve sizes greater than 30% and less than 40%, or yellowtail snapper fishery with a small reserve less than 15%. For any other reserve sizes or fisheries, there are not enough yield benefits within a ten year window to pay back any loan above a philanthropic rate (Fig.XX).

```{r, fig.cap= 'Maximum % interest rate payable by a fishery for each species across a range of terminal reserve sizes. Dashed line indicates break between philanthropic (<5%) and social investment (5%-15%) loans, above dotted line are commercial loans (>15%)'}
static__maxinterest_plot
```

The value increase experiment asks by how much the value of the fishery's catch would have to increase to completely offset the worst yield losses induced by the reserve in any given year. By extension then, that same value increase would more than offset any lesser losses occurring in other years. In contrast to the interest rate analysis, our results show value increases to be a promising solution for offsetting economic losses (Fig.XX). While the magnitude of the required value increase scales linearly with the size of the reserve, value increase of 20-30% are capable of completely offsetting short-term economic impacts of reserves up to 10-20% in size in nearly all the evaluated fisheries. The magnitude of price increases needed appears to be inversely related to the magnitude of NPB, implying that smaller value increases by me able to offset losses to species that were unable to achieve positive NPB through design.  

```{r, fig.cap= ' % Price increase required by a fishery for each species across a range of terminal reserve sizes'}
static__priceinc_plot
```

# Discussion

It has been well established that the ability of reserves to provide long-term benefits to fisheries is highly context dependent. Based on this literature, by simulating an overfished fishery with no capacity for additional management measure (such as size limits or effort restrictions), we ensure that our simulated fishery is greatly benefited by reserves in the long-term. However, we show that even in this context,the short-term fishery benefits are far less certain. For some species, and with smaller reserve sizes, our simulated fishery does perceive some short term benefits. But for many species, and for reserves of any substantial size (>20%), reserves were broadly unable to provide benefits soon enough to be worth the short-term losses in fishery yields to our hypothetical community. Explicit consideration of short-term economic impacts, through NPB, is a critical step in truly understanding the ways in which a reserve may affect fisheries. 

The specific results presented here are highly sensitive to particular choices in model parameters, such as discount rates, utility function, life history values, and fleet dynamics. As such, these findings are illustrative; the exact dynamics of the timing and magnitude of benefits may change greatly with different assumptions. A few key assumptions should be noted. First, we include no fishery management measures besides the reserve itself, in order to more clearly articulate the effects of the reserve. Addition of tuning of fishing mortality rates or selectivity may dramatically change results (or may be a broadly more ideal strategy than reserves if the only goal is improving fisheries). Further consideration of the best strategies for integrating reserves and other fishery management tools is warranted. We also assume an initial fishery condition of 0.15 B/B~MSY~. The ability of reserves to provide short-term (or long-term) benefits scales with the degree of overfishing; a more overfished setting would result in greater short-term economic benefits from rebuilding, while starting the fishery at a higher biomass would reduce them.

We use relatively simple fleet dynamics. We assume a fixed number of fishers that are concentrated outside the reserve following the implementation of a reserve. An alternative strategy would be to allow the fishing fleet to expand and contract in response to the profitability of fishing. Without management, we might assume then that any profit benefits generated by the reserve would be eventually offset by commensurate increases in fishing mortality, as more fishers seek to capture benefits created by the reserve. 

The choice of larval dispersal dynamics can dramatically affect the results of implementing a reserve. We do not directly incorporate source-sink dynamics, in which the reserve acts through currents are adult aggregations as a direct source of larvae to the fished and unfished parts of the system. However, the recruitment models used do allow species to have different reactions to the changes induced by the reserve. For example, we model red grouper density dependence at the regional level, mimicking regional spawning aggregations rather than allowing densities inside the reserve patches along to limit larval production of that species through patch-specific density dependence. We also assume that all larvae produced by the system are retained by the system, and do not migrate to areas outside the simulated community. 

These assumptions can and should be revisited in assessing the effect of reserves on individual fisheries. We believe though that on balance our assumptions favor the ability of reserves to provide benefits; as such these results are likely to be optimistic estimates of the timing and magnitude of short-term fishery benefits from reserves. Alternative hypotheses concerning the mechanisms through which reserves might act on fisheries should be tested through the context we propose to consider their short-term economic implications, before they are implemented in the field. 

Using our assumptions, our results show that even when long-term benefits are predicted to result from a reserve, it may take over a decade for the reserve to result in a net gain in fishing yields for the community. While this may be entirely acceptable to some communities, the discount rates reported by Johnson & Saunders [-@Johnson2014] and Curtis [-@Curtis2002] suggest that the magnitude of these eventual benefits would not be sufficient to offset the short-term losses required to achieve the gains. Presenting the evolution of net benefits over time as we have done allows researchers and decision makers to confront the potential economic impacts of a reserve, and determine whether a reserve of a particular size and design is likely to provide meaningful net benefits to a community. 

What species are more likely to provide short-term economic benefits then?  The silver trevally fishery was likely unable to benefit from the reserve due to the species' high movement rate, while the poor short-term economic performance of the blacknose shark fishery likely resulted from a combination of high movement rate and slow growth. The high ability of red throat emperor fishery to benefit from reserves likely derived from moderate movement rates and high growth rates, allowing some spillover to occur but still allowing the species to benefit, and benefit quickly enough, from the reserve protection. It is beyond the scope of this paper to fully assess the biological attributes that result in a species benefiting from the reserve, though future analyses could build on this work to suggest what species are most likely to provide net fishery benefits to community's over the short-term. 

Similar to Brown et al. [-@Brown2014], across species we show that the design of the reserve can improve the economic outcomes of a reserve, especially in the long-term (Fig.XX). Our results show though that a shrinking strategy is preferable for a community seeking to maximize the short-term economic benefits of a reserve. While reserves covering 20-30% of habitat often maximized long-term yields in our simulations, reserves with a terminal size less than 15% were preferable in terms of short-term economic benefits. In addition, even under optimal design a decade or more was often required to achieve positive NPB, if positive NPB was possible at all. We do show though that applying a common reserve size across multiple species did not dramatically reduce the utility of the fishery, so long as the reserve implemented is optimal for at least one species.

Taken together then, our study finds little evidence that careful design of the size of a reserve over time is the solution for reducing or eliminating the short-term economic fishery impacts of implementing a marine reserve. While design can improve outcomes, within a range of smaller reserves design is unlikely to move a fishery from having a dramatically negative to a large positive NPB. Relying on design alone, we should be cautious in expecting short-term economic benefits from reserves. 

Our results indicate that loans are unlikely to be viable alternative for offsetting short-term economic losses. In most instances, the interest rate a community could afford to pay on a 10-year loan was too low to be viable for anything but a philanthropy backed loan. While specific instances might make a loan viable, the cases in which the benefits from a reserve sufficiently outweigh the short-term costs to make  loan viable appear to be the exception. This also does not account for the logistical challenges of providing and managing a loan for a community such as the one modeled here.

Value increases were the most viable solution to the short-term economic losses of reserves that we identified. Increases in value of 15-30% appear capable to completely offset yield losses for reserves covering up to 25% of the fishery (and would come close to offsetting larger reserves). It is especially interesting to note that the fisheries that had the worst economic outcomes from reserves, such as blacknose shark and silver trevally, had the lowest required increases in value. While these value increases are not trivial, they are not entirely implausible. Better care of fish, for example through careful icing that might not be ordinarily available to a community, can boost value by XX%. Retailers may also pay a price premium of XX% for sustainably managed fish. Alternatively, increased efficiency, for example through coordination of fishing efforts rather than derby-style fishing, can reduce costs by XX%. Or, fishermen could attempt benefit from reserve-based tourism, either through changing livelihoods or through tourism fees, which may be able to provide sufficient increases in their net income enough to offset fishing losses [@Sala2013].  While all of these solutions face challenges in the developing world, these hurdles are less significant than the challenges (and limited potential) of optimizing design, or attempting to obtain and successfully repay reserve-based loan. 

From the perspective a community leader of an artisnal fishery, our results show that it is difficult for reserves alone to provide sufficient benefits quickly enough to offset the short-term economic losses induced by closing off fishing grounds. This result should not be taken as an indictment of reserves, but rather a call for clear analyses and communication of the real impacts of reserves to fishing communities. There are many documented benefits reserves can provide to and beyond fisheries, from providing conservation benefits and ecological resilience, to increased tourism potential. In some cases the societal benefits of conservation and tourism gains from the reserve may well outweigh fishery losses. In addition, as in the overfished case modeled here, reserves can provide fishery benefits in the long-term.

It is imperative though that those engaged in the design and implementation of reserves carefully consider and communicate the short-term impacts of reserves on the economic well-being of affected fisheries. It is misleading to tell a community that a reserve will provide fishery benefits, but neglect to point out that those benefits may not accrue for over a decade. In addition, support and enforcement of a reserve may quickly dissipate if a reserve does not begin to provide net economic benefits to a community on the time scale fishermen were expecting. The NPB framework presented here is an important tool for assessing the short-term economic impacts of a reserve. Discussing the timing and magnitude of benefits stemming from reserves allows stakeholders to directly confront the challenges, and consider what solutions may be on the table given their circumstances. Our results indicate that rather than focusing on eliminating short-term losses through careful design, or counting on future benefits to finance fishery improvement loans, more potential lies in helping communities increase the value of their catch or leverage tourism opportunities to offset reserve induced losses. 

# Acknowledgements

We are grateful for assistance and guidance from Lennon Thomas, Sarah Lester, Chris Costello, and Steve Gaines. DO was supported by a grant from the Waitt Foundation and the Daniel and Dianne Vapneck Fisheries Management Fellowship. 

# Works Cited

---
nocite: | 
 @SEDAR2011, @Kobayashi2011, @SEDAR2009, @Leigh2006, @Rowling2000, @OHop2012
...

