---
title: "Solutions for the Short-Term Economic Impacts of Marine Reserves"
author: "Dan Ovando, Dawn Dougherty, Jono Wilson"
date: "July 9, 2015"
output:
  pdf_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 8
  html_document:
    fig_align: center
    fig_caption: yes
    fig_height: 6
    fig_width: 8
  word_document:
    fig_caption: yes
    fig_height: 4
    fig_width: 6
header-includes:
- \usepackage{setspace}
- \doublespacing
- \usepackage{lineno}
- \linenumbers
number_sections: yes
csl: fish-and-fisheries.csl
bibliography: MPA Benefits.bib
toc: yes
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.path='Figs/', echo=FALSE, warning=FALSE, message=FALSE)
```
```{r}
library(gridExtra)
library(ggplot2)
library(dplyr)
library(tidyr)
library(knitr)
ModelRun <- 'Full Grid 2.2'

load(paste('Results/',ModelRun,'/NutsPlots.Rdata',sep = ''))

#####Example Shrinking NUTZ concept

CartoonPlot<- function(Theme)
{

r=0.24
K=100
Nvec=NA
Nvec[1]=K
u1=0.16
u2=0.12
yvec=NA

for(t in 2:150){
  if(t<100)u=u1 else u=u2
  Nvec[t]=Nvec[t-1]+r*Nvec[t-1]*(1-Nvec[t-1]/K)-u*Nvec[t-1]
  yvec[t-1]=u*Nvec[t-1]

  }



Years=1:149
Nvec=Nvec[1:149]
Yield=(yvec-yvec[98])/max(yvec)                 #creat standardized deviations from status quo
Biomass=(Nvec-Nvec[98])/max(Nvec)
dat=data.frame(Years,Biomass,Yield)

datA=subset(dat,Years>90 & Years<=149)
 datA$Years=-7:51
 
 datA$Balance=cumsum(datA$Yield)

#find year balance is positive for shaded area cutoff
test=subset(datA,Years>0)
test$flag=0
test$flag[test$Balance>0]=1
test$dup=duplicated(test$flag)
breakeven=which(test$dup==FALSE)[2]
breakYear=test$Years[breakeven]



#
#long format
longdat <- reshape(datA[,1:3], 
  varying = c("Biomass","Yield"), 
  v.names = "value",
  timevar = "Objectives", 
  times = c("Biomass","Yield"), 
  direction = "long")

 


p <- ggplot(longdat, aes(x=Years,y=value))

p + geom_area(data=subset(longdat,Years<=12 & Objectives=="Yield"),  fill="darkorange")+ geom_area(data=subset(longdat,Years>=12 &Years<=breakYear& Objectives=="Yield"),  fill="cornflowerblue")+ geom_line(aes(colour=Objectives),size=1.1)+ geom_vline(xintercept = 30,linetype=2) + scale_color_manual(values=c("aquamarine3", "black"))  + ylab("Deviation from Status Quo")  + scale_x_discrete(breaks=c(0,30),labels=c("0","Yield Balance"))     + scale_y_continuous(limits=c(-0.1, 0.2),breaks=0) + Theme
}


```

# Note

 * Play with the discount rate to include the biomass stuff, to show that the biomass goes up
 * The most robust reserve 
 * Cap interest rate at 25%
 * Loans 
 * Show trajectory with and without the price increase
 * Put cartoon back in 
 * fig 4 out
 * make figure 5 colored by timing to benefit 
 *
 
 1. Cartoon
 2. Discount
 3. NPB
 4. Trajectories
 5. Price
 6. Loan
 7. Cross species
 
 

# Abstract

Well-managed fisheries are critical for supporting healthy ocean ecosystems, coastal livelihoods, and food security for millions of people. Many communities lack the resources to implement effective fisheries management. No-take marine reserves are a relatively simple tool to conserve biodiversity and provide fishery benefits. While the long-term effects of reserves on fisheries have been well studied, the short-term economic impacts of establishing marine reserves are rarely considered.  In this paper we simulate fisheries for six species commonly caught in coastal fisheries in order to demonstrate the time required for a no-take reserve to provide a net improvement in the economic well-being of a fishing community. Our results show that while conservation benefits accrue rapidly, more than a decade is often required to provide net fisheries benefits, even under circumstances favorable for reserves. We explore a suite of strategies for mitigating these short-term economic losses, including flexible reserve designs, loans, and value increases. Our results indicate that reserves may struggle to provide short-term economic benefits to artisnal fisheries, and value increases show the most potential for offsetting these losses. Our findings provide mechanisms for improving the communication and use of no-take marine reserves as tools for fisheries management and conservation. 

# Introduction

More than 260 million people across the globe earn their livelihood in fishing related industries [@Teh2014]. Fish is a primary source of protein to over one billion people [@FAO2011]. Yet the sustainability of the fishing industry and the potential for wild capture fisheries to indefinitely feed a growing population is dependent on the implementation and enforcement of effective systems of governance and management. No-take marine reserves (hereafter reserves), areas set off-limits to fishing, are a widely used tool for protecting fish populations and are known to provide key conservation benefits that can improve ecosystem services to coastal environments. Conservation benefits of marine reserves include the maintenance of spatial population structure of fish stocks [@Berkeley2004; @White2008; @Rassweiler2012], protection of essential fish habitat, increased species diversity and fish biomass [@Lester2009], and can serve as reference areas to set local management regulations and disentangle the effects of fishing from environmental variability [@Wilson2013]. Enhanced biological production inside reserves can benefit adjacent fisheries through adult spillover [@Roberts1991; @Allison1998; @McClanahan2008] and larval export [@Cudney-Bueno2009; @Pelc2010], especially in situations where the size of the reserve is larger than the adult home range size, and smaller than the scale of larval dispersal [@Gerber2003]. Reserves can also serve as a hedge against changes in environmental conditions [@Stefansson2005; @Costello2008] and as an effective means of protecting spatially complex marine populations [@White2008; @Rassweiler2012]. 

Marine reserves can serve as a mechanism for simultaneously achieving conservation outcomes and improving the productivity of fisheries [@Gaines2010]. The case for using reserves for both conservation and fishery management is often made in the context of developing world fisheries, which may have little capacity to perform more complex fishery management practices (such as quotas, size limits, or effort restrictions) [@Holland1996]. In fact, reserves have a long history as fishery management tools in many island nations [@Johannes1978; @Johannes2002]. However, the ability of marine reserves to provide fishery benefits is dependent on a suite of factors, including the size of reserve relative to the home range size of the species, the dispersal potential, geographic extent of the stock, as well as the status of the fishery prior to implementation of reserves [@Sanchirico2001; @Costello2008; @White2008; @Rassweiler2012; @Sanchirico2006; @Smith2003]. Moreover, the implementation of marine reserves necessarily reduces the spatial extent of the fishery, often limiting take in prime fishing grounds and concentrating effort into smaller regions of the coast [@Halpern2004]. 

The potential and challenges of utilizing reserves as fishery management tools have been well studied [@Hilborn2004], though it is worth noting that the vast majority of this work is simulation based, and little empirical evidence of the fishery impacts of reserves is available [see @Fletcher2014 for an empirical paper that found no evidence of enhanced fishery production from the Great Barrier Reef marine reserve]. There is a critical gap in the the literature concerning fisheries and reserves though; the economic impacts over time. Nearly all of the published research on the topic has considered the long-term (or equilibrium) economic impacts of implementing a marine reserve (note that for this paper, the we refer solely to fishing when we consider economic impacts). 

However, while the long-term impacts are critical to understanding the interactions between reserves and fisheries, from the perspective of fishing communities the short-term impacts may be of much greater consequence. Depending on the time horizon that a community is able or willing to consider, a reserve that provides long-term fishery benefits may provide no practical benefit to today's fishers and decision makers. Alternatively, even in conditions in which a community will perceive benefits in the future, they may have to endure years of reduced fishing income and food until those benefits arrive.These short-term consequences of reserves can have profound implications on the financial health and food security of fishing communities, affecting local support and buy in for enforcement policies, trust in management and supporting organizations, and ultimately the sustainability of the fishery itself. 

Brown et al. [-@Brown2014] provides an important contribution to our understanding of the short-term impacts of marine reserves. They illustrate that there are often important tradeoffs between short-term and long-term economic fishing benefits from reserves, and that alternative strategies for designing those reserves (how large they are and how that size changes over time) can affect the short-term economic effects of a reserve. Brown et al. [-@Brown2014] launches an important discussion on the ways in we might choose to design reserves in order to provide fishery benefits, and the ways in which the consequences of those choices can be communicated to fishing communities. In particular, they point out that reserves designed around long-term benefits have substantial short-term costs. Our paper builds on this work by focusing on potential solutions to the trade-offs identified by Brown et al. [-@Brown2014]. 

We ask whether reserve design and financial mechanisms can reduce or offset the short-term economic costs of marine reserves. We analyze these questions by using a simulated developing world fishery targeting a variety of typical tropical reef species. We focus on artisanal fisheries such as these, since small-scale fisheries throughout the developing tropics are often targetted as sites for reserve based management. We find that reserves may struggle to provide net fishing benefits at a time scale that is of value to fishing communities for many common reef associated fish species, and financial mechanisms may be needed to offset these losses.

# Methods

## Operating Model

We analyzed 6 different species, intended to capture a range of life-history traits of species often targeted by tropical developing country fisheries. Our model is single species, age-structured and assumed to be closed with respect to larval and adult emigration and immigration. The spatial configuration of the fishery includes 100 unique patches with wrapped edges connected by larval and adult movement. The model tracks stock numbers, biomass,  fishery yields over time. 

Life history values were drawn from stock assessments where possible, in order to help ensure reliable and consistent values(Table.1). The recruitment model (or the functional for of the density dependence relationship) was selected from the possible structures outlined in Babcock & MacCall [-@Babcock2011] using expert judgement.  The *Range* parameter scales the number of patches moved by adults in a time step, with 100% indicating total mixing and 0% a completely sedentary species. 

```{r}

LifeHistories <- read.csv('Inputs/Life History Inputs.csv',stringsAsFactors = F)

LifeVars <- c('CommName','Range','m','k','Linf','t0','AgeMa50','LengthMa50','BH.Steepness','DDForm','Source')

LifeTable <- LifeHistories[, LifeVars] %>%
  rename(Species = CommName, h = BH.Steepness)


LifeTable$DDForm[LifeTable$DDForm == 'Babcock1'] <- 'I'

LifeTable$DDForm[LifeTable$DDForm == 'Babcock2'] <- 'II'

LifeTable$DDForm[LifeTable$DDForm == 'Babcock3'] <- 'III'

LifeTable$DDForm[LifeTable$DDForm == 'Babcock4'] <- 'IV'

LifeTable$DDForm[LifeTable$DDForm == 'Babcock5'] <- 'V'

LifeTable$DDForm[LifeTable$DDForm == 'Shark'] <- 'I'

LifeTable$DDForm <- paste(LifeTable$DDForm, '*',sep = '')

LifeTable <- LifeTable %>% 
  rename('Recruitment Model' = DDForm)

LifeTable$Range <- paste(100*LifeTable$Range, '%',sep = '')

LifeTable$Range <- paste(LifeTable$Range, '*',sep = '')

kable(LifeTable, digits = 2, caption = 'Life history values used. m is natural mortality, Linf, k, and t0 are the Von Bertalanffy growth parameters, Age/Length Ma50 are the respective age or length at which the 50% of the individuals have reached sexual maturity, h is steepness, and the roman numeral under "Density Dependence" corresponds with the density dependence form from Babcock & MacCall 2011 that was used. Values with * were assumed')

```

The number of fish in patch i at age a at the beginning of year t+1 is

(1) $N_{i,a,t+1} = R_{i,t+1}$ if *a = 0*

(2) $N_{i,a,t+1} = N_{i,a-1,t}e^{-M-F_{i,t}\upsilon_{a-1}}$  if $1 \leq a < x$

(3) $N_{i,a,t+1} = N_{i,x-1,t}e^{-M-F_{i,t}\upsilon_{x-1}} + N_{i,x,t}e^{-M-F_{i,t}\upsilon_{x}}$  if $a = x$

where *R~i,t~*is the recruitment in patch *i* in year *t*, *F~i,t~* is the instantaneous fishing mortality in patch *i* in year *t*, $\upsilon_{a}$ is the selectivity of the fishing gear for a fish at age *a* (which we assume to be 1 for all ages),  *M* is the instantaneous natural mortality, and *x* is the maximum age recorded in the model (the plus group). This model assumes that the biological parameters of each species are homogeneous across space and time.

The simulations begin at an unfished equilibrium using a specified unfished initial recruitment in each patch *i*, *R~i,0~* such that

(4) $N_{i,a} = R_{i,0}$ if *a = 0*

(5) $N_{i,a} = N_{i,a-1}e^{-M}$  if $1 \leq a < x$

(6) $N_{i,a} = \frac{N_{i,x-1}e^{-M}}{1-e^{-M}}$  if $a = x$

The population is then fished down at a specified open access harvest rate in both patches to equilibrium conditions. We set this rate such that biomass over biomass at maximum sustainable yield (B/B~MSY~) is equal to 0.25 at equilibrium, representing an overfished fishery. We chose this level as the benefits of reserve formation were positively (and relatively linearly) related to the degree of overfishing. Starting at an overfished state then provides an optimistic estimation of the potential benefits of reserve formation.  

The average length (*l~a~*) of fish in each age class is calculated using a von Bertalanffy growth equation

(7) $l_{a} = L_{inf}(1-e^{-k(t-t_{0})})$

and then converted to average weight (*w~a~*) using:

(8) $w_{a}=b_{1}l_{a}^{b_{2}}$

We assume habitat quality to be the same in all patches.  Adult movement at each time step among the 100 patches is then calculated using a Gaussian dispersal kernel 

(9) $p_{i,j}=e^{\frac{-d_{i,j}^{2} }{2\sigma_{A}^{2}}}$

where *p~i,j~*  is the proportion of fish moving from area *i* to area *j*,  and *d~i,j~* is the distance between area *i* and area *j*. The model parameter $\sigma_{A}$ defines the movement range for the species, and is scaled by the *Range* parameter. We wrap movement in order to remove edge effects. The relative proportions are then normalized so that the total proportion of fish moving from area *i* to any area sum to one. The number of fish in each age group one and older after movement are then

(10) $N_{i,a,t} = \sum^{100}_{j=1} N_{j,a,t}p_{i,j}$

To calculate recruitment each year in each patch we use the recruitment models described in Babcock & MacCall [-@Babcock2011], in order to allow the nature of density dependence to vary among species (for example, pre or post settlement density dependence). 

## Fishery Dynamics

The catch in each patch at each time step is calculated as

(11) $Y_{i,t} = \sum_{a}(N_{i,a,t}e^{-F_{i,t}\upsilon_{a}})$ 

We assume a closed population of fishers, where the number of fishers does not change with the implementation of a reserve (no emigration or immigration of boats), such that the effort from the reserve area is displaced to the fished area. This is intended to reflect a subsistence style fishery, with few alternative livelihoods besides fishing. Fishing effort is scaled by the relative commercial biomass,$\bar{B}_{i}$, in each patch where

(12) $\bar{B}_{i}= \frac{B_{i}}{\sum_{i}B_{i}}$

(13) $F_{i,t}=F_{pNTZ}(1+P_{NTZ})\bar{B}_{i}$

Where *F~pNTZ~* is the total possible instantaneous fishing pressure in the patch before the implementation of the reserve, and *P~NTZ~* is the fraction of patches that are in a reserve. 

## Reserve Implementation

We simulate a series of reserve implementation scenarios using the above operating model and fleet dynamics. A given scenario is defined by an terminal reserve size (% of area in a reserve), an "intercept" (% of the area in a reserve in year 1), and a "slope" (% of run years at which the reserve reaches terminal size). In effect then we allow the final size, initial size, and rate at which the reserve reaches its final size to vary. We apply a fine-scale grid of factorial combinations of reserve size, intercept, and slope to each of the 6 species included in this paper, providing an outline of the potential outcomes of reserve implementation. 

## Metrics

Throughout each scenario we keep track of live biomass of fish in the water and fishery yields over time. Net present balance (NPB) is our primary metric of performance, where NPB represents the present value of the cumulative yield benefits of a given reserve strategy relative to the status quo, calculated as

(14) $NPB_{s} = \sum^{T}_{t=0} \frac{Y_{s,t}-Y_{q}}{(1+r)^{t}}$

for any given species, where *t* is time, *Y* represents fishing yields, *s* is reserve implementation strategy, *q* is the status quo, *r* is the economic discount rate, and *T* is a specified number of years after reserve implementation in which *NPB* is calculated and compared across scenarios and species. We calculate the year at which NPB surpasses zero (increased benefits have compensated for short-term losses). NPB is an important output, since it reflects the net benefit that a community perceives from a given reserve strategy, relative to their benefit without the reserve. Alternatively, present balance (PB), the discounted difference between yields of a given reserve strategy and the status quo in year t, while important and a commonly presented metric, may not be as meaningful to a community (e.g. a 1 ton improvement over the status quo in year 10 of a reserve strategy may be of little value if 1,000 tons have been lost in years 1 through 9; see Fig.1 for an illustration of these concepts). **Dawn walk us through cartoon illustration here**

```{r, fig.cap= 'Illustration of the trajectory of yield and biomass benefits following a reserve'}
Cartoon <- CartoonPlot(SimpleTheme)
Cartoon
```

## Financial Mechanisms

We also analyze two potential financial mechanisms for offsetting short-term fishery losses stemming from the reserve; a loan system and a value added system. The total relative loss in yields experienced by the fishery for a given scenario *s* is 

(15) $O_{s} = -\sum^{T}_{t=0} min(0,Y_{s,t}-Y_{q})$

Where *O~s* is the amount of yield lost relative to the status quo over time period *T*. Under the loan strategy, a non-governmental organization, government, or private investor could provide a community with a loan to offset the initial losses from implementing a reserve, with a goal of being repaid by the future fishery benefits resulting from enhanced fishery productivity. The fishing community requests a loan totaling *O~s~*. The surplus available to pay the loan back over time *T* are equal to 

(16) $S_{s} = -\sum^{T}_{t=0} max(0,Y_{s,t}-Y_{q})$

Where *S~s~* is the total positive difference in yields (if any) for a given reserve scenario *s*,over what the fishery would have experienced under the status quo.

For a given loan interest rate *i* for a loan of duration *T*, the total loan payments are equal to 

(17) $C = Tp( \frac{\frac{i}{p}{O}}{1-(1+i)^{-Tp}})$

where *p* is the number of payments per year. Setting the time window of the loan to *T* of 10 years with *p* of 4 payments per year, we then use the *optim* package in *R* [@RCoreTeam2015] to estimate the highest interest rate *i* (%) that the community could afford in order to pay back a 10-year loan such that *C~s,i~ <= S~s~*; meaning that the total loan payments must be less than or equal to the surplus generated by the reserve. The higher the maximum potential interest rate, the more viable the loan is. 
 
For the value increase scenario, we implicitly assume a status quo value of $1 per unit weight (though this is an arbitrary choice that does not in fact matter). We then ask by what percent the value of the catch caught under a given scenario *s* would have to increase in order to completely offset the greatest loss of yields seen across all years

(18) $P_{s} = 100(\frac{Y_{q}}{Y_{q}+min(Y_{s}-Y_{q})}-1))$

Reserves often face competing objectives between long-term conservation benefits and short-term economic benefits. This can be empirically illustrated by considering the cumulative biomass of fish in the water over time with a discount rate *r* of 0 (long-term conservation planner, $B_{r_{0}}$) vs. the net present benefits of the reserve over time with a discount rate *r* > 0 (in this case we consider 0.1, $Y_{r_{0.1}}$)). In order to consider the relative utility of a given reserve strategy *s* we assign a weighting parameter $\alpha$ that can take any value from 0 to 1, such that total utility *U* is calculated as

(19) $U_{s} = \alpha(\frac{Y_{r_{0.1},s}}{\sum_{s}Y_{r_{0.1},s}}) + (1-\alpha)(\frac{B_{r_{0},s}}{\sum_{s}B_{r_{0},s}})$

This allows us to calculate utility focused solely on discounted fishery benefits ($\alpha$=1), long-term conservation benefits ($\alpha$=0), or any relative weighting in between). 

# Results

## Discount Rate

We first provide an illustration of the importance of the assigned discount rate *r*, using yellowtail snapper (Fig.XX). The discount rate reflects the degree to which money today is favored over money tomorrow; the higher the rate, the less a community (or individual) values something in the future relative to today. For a given discount rate, we find the reserve scenario *s* (combination of terminal size, starting size, and slope) that maximizes the community's utility per Eq.19 (using $\alpha = 0$). With a discount rate of 0 (which means that a dollar in the future has the same value as a dollar today) the NPB is simply the cumulative sum of the yield balances over time. Under this scenario, the optimal policy for yellowtail snapper is to put a substantial portion of the fishery into a reserve for nearly a decade, reducing the reserve size once the fishery begins to recover, resulting in substantial economic gains for the fishery by year 50. 

A discount rate of 0.05 is the default value in much of the economic literature (CITATION XXX). Under this reality, the optimal reserve scenario from the perspective of a community designing a reserve today would be to implement a reserve covering ~50% of the fishery, and then reduce it's size more quickly than under the *r*=0 scenario. This strategy results in a positive NPB for the community in slightly over 10 years, meaning that from the community's perspective, they would need to feel confident that they will be there and fishing for at least 10 years in order for a reserve based around yellowtail snapper to be worthwhile for them (Fig.XX)

However, our thought experiment for this study is the management of an artisnal fishery using reserves. While few studies have actually estimated the discount rate for artisanal fishers, those that have report much higher discount rates than 0.05; Johnson & Saunders [-@Johnson2014] and Curtis [-@Curtis2002] found discount rates of artisnal fishermen of ~0.22 (mean) and ~ 0.35 (median), respectively, meaning that the fishermen in those studies value profits today much more than profits tomorrow. With this in mind, we can then consider the case of a discount rate of 0.2 for this yellowtail snapper fishery. Under this scenario, the NPB maximizing strategy is still to shrink the reserve over time, but the reserve starts at only ~25%, and shrinks to almost nothing. The reserve is able to provide almost no net benefit to the community, as the benefits occur too far in the future to be of value today (Fig.XX)

```{r, fig.cap='Example NPB trajectories under optimal reserve scenario under different discount rates for yellowtail snapper'}

discount_rate_plot

```

## Solutions to Short-Term Losses

Clearly then the choice of discount rate greatly impacts a community's perception of the ability of a reserve to provide benefits to their fisheries. For the remainder of this thought experiment we consider a discount rate of 0.2, to best reflect the type of artisanal fishery we are simulating. With this discount rate in mind, how does the final size of the reserve affect a community's NPB? Under this thought experiment, the community picks one reserve size, ranging from 2.5% to 50% of the available habitat, and immediately implements it. We apply this procedure to each of the 6 species evaluated here, running over a 50 year time horizon. 

Our results show that with a discount rate of 0.2, only the red throat emperor and yellowtail snapper fisheries are capable of providing positive NPB to the community under any of the evaluated reserve sizes (Fig.XX). Red throat emperor is the most promising; reserves covering less than 35% of the fishery all benefit the fishery within 15 years, with peak benefits occurring at 15% reserve coverage. Positive NPB is possible for yellowtail snapper, but only for reserves covering less than 5% of the fishery, and even then the net benefit is small, and takes ~20 years to arrive. Reserves are not a worthwhile strategy for managing the fishery for any of the other evaluated species; while each of the species evaluated here would see a net benefit in the future from some reserve size, the benefits occur too far in the future to be of relevance to community decision makers today (Fig.XX)

```{r, fig.cap= 'NPB with discount rate of 0.2 under possible terminal reserve sizes for each species'}
static_NPB_plot
```

A single reserve size implemented today is not an ideal strategy for our hypothetical community decision maker for nearly any species evaluated here; the benefits simply accrue too far in the future, so our manager would rather maintain the overfished status quo than forgo yields today, even though the absolute future benefits are substantial. Brown et al. [-@Brown2014] suggest that one solution to offsetting short-term losses may be to allow the reserve size to change over time. To that end, we consider the potential benefits to our community from allowing the reserve to change sizes over time. We set $\alpha$ to 0.9, meaning that 90% of the community's utility comes from fishery benefits, but some consideration is made for long-term conservation outcomes. 

We find that while dynamic designs can improve the outcomes, red throat emperor and yellowtail snapper remain the only fisheries that receive a net benefit from the reserve. Interestingly, and in contrast to Brown et al. [-@Brown2014], which explored a growing reserve as a solution to short-term economic losses, we find that the optimal strategy for a reserve that is capable of any positive NPB is to start at a larger reserve size and decrease in size over time (Fig.XX. Using this shrinking strategy red throat emperor and yellowtail snapper are able to achieve substantial increases in yields relative to status quo and a positive NPB. Yields break even in approximately 5 years, though net benefits, the metric of primary concern to most community's, takes longer to arrive (~8 and 15 years, respectively). 

For the other species, even a allowing the reserve to shift sizes over time does not allow the community to see a positive net benefits. While in all cases fishery catches in the future are greater than fishery catches today, these benefits occur too far in the future to offset the short-term losses; making the reserve a poor choice from the perspective of a community decision maker today (Fig.XX) 

```{r, fig.cap='NPB trajectories under optimal reserve scenario. Size of circle represents % of ares in reserve, color the yield surplus in a given year'}

opt_npb_plot

```

Our results so far provide three important points; 1) All the evaluated species in our hypothetical fishery are capable of benefiting in the long-term from a reserve but 2) those benefits take too long to arrive to be of value to a decision maker today and 3) optimal design can improve outcomes, but does not sufficiently accelerate the arrival of fishery benefits to make a reserve worthwhile to a fishing community. What if we then shift our focus from designing reserves to prevent fishing losses, but instead considered strategies to offset the reserve-induced losses that our results show are likely to occur for many species in our hypothetical fishery?

Suppose the community was able to organize itself into and apply for a loan capable of covering the net yield losses imposed by the creation of a reserve (Eq.XX). For this scenario we once again consider a single reserve size, since we have seen that allowing the reserve size to change over time does not greatly alter results (Fig.XX). The community's goal would be to pay back that loan using the eventual yield increases (Eq.XX) over a ten year period with four payments per year. We find that under these assumptions, loans are not a viable strategy for offsetting the short-term economic losses of the reserve. 

Similar to the NPB results (Fig.XX), loans are viable only for red throat emperor and yellowtail snapper. In the case of red throat emperor, the community could afford to pay back a loan at very high interest rates, up to and above 25%,if the reserves is less than 25% of the area. Under these rates the community could possible afford to take a loan out from a commercial bank to pay for the short-term yield losses of the reserve. Social investment loans (interest rates >5% and less than 15%) might be viable for red throat emperor with reserve sizes greater than 30% and less than 40%, or yellowtail snapper with a small reserve (5%). For any other reserve sizes or species, there simply are not enough yield benefits within a ten year window to pay back a loan with any realistic interest rate. 

```{r, fig.cap= 'Maximum % interest rate payable by a fishery for each species across a range of terminal reserve sizes'}
static__maxinterest_plot
```

Increasing the value of a community's catch may provide another path to offsetting the short-term economic losses of a reserve, per Eq.XX . Under this scenario, increases in value could be achieved by improving the quality of the catch (e.g. providing an ice plant), providing access to more lucrative markets (e.g. seafood distributors committed to sourcing sustainably), or reducing costs (e.g. through coordinated fishing efforts). Our results show value increases such as these to be a promising solution for offsetting economic losses (Fig.XX). While the magnitude of the required value increase scales linearly with the size of the reserve, value increase of 20-30% are capable of completely offsetting short-term economic impacts of reserves up to 20-30% in size in nearly all the evaluated species. 

```{r, fig.cap= ' % Price increase required by a fishery for each species across a range of terminal reserve sizes'}
static__priceinc_plot
```

All our results so far have considered each of the species in isolation. In reality many artisanal fisheries are likely to target multiple species. To account for this, we lastly consider the economic impacts of a reserve scenario designed around one species but applied to all six of the fish considered here (Fig.XX). For each of the six species included here, we find the utility maximizing reserve strategy. We then apply that optimal strategy to each of the other species, and asses detrimental that strategy is when applied to species for which it was not designed. 
We find that the outcomes for a given species are relatively insensitive to application of another specie's optimal reserve policy; this means that using a reserve designed around yellowtail snapper to manage blacknose shark only reduces the utility of the blacknose shark fishery by ~5%, relative to the highest utility that the blacknose shark fishery could achieve (Fig.XX). The silver trevally designed reserve (terminal size of 15%) is the most robust of the possible scenarios when applied to all the other species in the study. 

```{r, fig.cap= 'Comparison of NPB performance for each species using the other species optimal reserve'}
species_comp_plot
```

# Discussion

It has been well established that the ability of reserves to provide long-term benefits to fisheries is highly context dependent and uncertain. By simulating an overfished fishery with no capacity for additional management measure (such as size limits or effort restrictions), we ensure that our case-study fishery is in fact capable of being benefited by reserves in the long-term. However, we show that even in this context, short-term fishery benefits are far from certain. From the perspective of a community decision makers with a representative high discount rate, reserves of any substantial size do not provide benefits soon enough to be worth the short-term losses in fishery yields. 

The specific results presented here are highly sensitive to particular choices in model parameters, such as discount rates, utility function, life history values, and fleet dynamics. As such, these findings are illustrative; the exact dynamics of the timing and magnitude of benefits may change greatly with different assumptions. A few key assumptions should be noted. First, we include no fishery management measures besides the reserve itself. Addition of tuning of fishing mortality rates or selectivity may dramatically change results. We felt that it was better to isolate the fishery effects of the reserve alone for the purposes of this paper, though further consideration of the best strategies for integrating reserves and other fishery management tools is warranted. We assume an initial fishery condition of 0.25 B/B~MSY~. The ability of reserves to provide short-term (or long-term) benefits scales with the degree of overfishing; a more overfished setting would result in greater short-term economic benefits from rebuilding, while starting the fishery at a higher biomass would reduce them.

We also use relatively simple fleet dynamics. We assume a fixed number of fishers that are concentrated outside the reserve following the implementation of a reserve. An alternative strategy would be to allow the fishing fleet to expand and contract in response to the profitability of fishing. Without management, we might assume then that any profit benefits generated by the reserve would be eventually offset by commensurate increases in fishing mortality. 

Lastly, we do not directly incorporate source-sink dynamics, though the recruitment models used do allow species to have different reactions to the changes induced by the reserve. For example, we model red grouper density dependence at the regional level, mimicking regional spawning aggregations rather than allowing densities inside the reserve patches along to limit larval production of that species through patch-specific density dependence. 


While these caveats can and should be revisited in assessing the effect of reserves on individual fisheries, our broader approach allows us to consider several broader conclusions.First, it is critical to consider the discount rate, or more broadly the ability and willingness of a community to forgo current yields for future benefits, and the timing of reserve-induced benefits in communicating the potential economic fishery impacts of a reserve. Our results show that even when long-term benefits are predicted to result from a reserve, it may take over a decade for the reserve to result in a net gain in fishing yields for the community. While this may be entirely acceptable to some communities, the discount rates reported by Johnson & Saunders [-@Johnson2014] and Curtis [-@Curtis2002] suggest that the magnitude of these eventual benefits would not be sufficient to offset the short-term losses required to achieve the gains. Presenting the evolution of net benefits over time as we have done allows researchers and decision makers to confront the potential economic impacts of a reserve, and determine whether a reserve of a particular size is likely to provide meaningful net benefits to a community. 

What species are more likely to provide short-term economic benefits then?  Species such as silver trevally likely were unable to benefit from the reserve due to their high movement rate.. **How much do we want to go into hypothesizing about this**?

Across species, similar to Brown et al. [-@Brown2014], we show that the design of the reserve can improve the economic outcomes of a reserve, especially in the long-term (Fig.XX). However, design alone does not appear to be capable of dramatically changing outcomes in the short-term; either a species is suited for achieving short-term benefits from reserves or it is not. For the majority of the species considered here, reserves were unable to result in a positive NPB for the community, even when optimally designed. In the case of red throat emperor though, the species appears to be broadly amenable to any reserve strategy that results in less than 30% of the habitat protected. Yellowtail snapper was the only species that was somewhat "on the fence", in that the specific design of the reserve could quickly shift the NPB of the fishery from positive to negative. On the positive side though, it appears that applying a sub-optimal reserve to a species does not dramatically alter its NPB, suggesting that for an array of reserve sizes from the 10-15% range the results are likely to be similar for the suite of species evaluated here (though those results may not be good).

Taken together then, our study finds little evidence that careful design of the size of a reserve over time is the solution for reducing or eliminating the short-term economic impacts of implementing a marine reserve. While design can certainly help, design is unlikely to move a fishery from having a dramatically negative to a large positive NPB, though no species saw positive NPBs when the final reserve size was greater than 30%. What about financial mechanisms then? Our results indicate that loans are unlikely to be viable strategies for offsetting short-term economic losses. In most instances, the interest rate a community could afford to pay on a 10-year loan was too low to be viable for anything but a philanthropy. While specific instances might make a loan viable, the cases in which the benefits from a reserve sufficiently outweigh the short-term costs to make  loan viable appear to be the exception. 

Value increases were the most viable solution to the short-term economic losses of reserves that we identified. Increases in value of 15-30% appear capable to completely offset yield losses for reserves covering up to 25% of the fishery (and would likely come close to offsetting larger reserves). It is especially interesting to note that the fisheries that had the worst economic outcomes from reserves, such as blacknose shark and silver trevally, had the lowest required increases in value. While these value increases are not trivial, they are not entirely implausible. Better care of fish, for example through careful icing that might not be ordinarily available to a community, can boost value by XX%. Retailers may also pay a price premium of XX% for sustainably managed fish. Alternatively, increased efficiency, for example through coordination of fishing efforts rather than derby-style fishing, can reduce costs by XX%. Or, fishermen could attempt to pivot livelihoods and start engaging in reserve-based tourism, which may be able to provide sufficient increases in their net income enough to offset fishing losses [@Sala2013].  While all of these solutions face challenges in the developing world, these hurdles are less significant than the challenges (and limited potential) of optimizing design, or attempting to obtain and successfully repay reserve-based loan. 

From the perspective a community leader of an artisnal fishery, our results show that it is difficult for reserves alone to provide sufficient benefits quickly enough to offset the short-term economic losses induced by closing off fishing grounds. This result should not be taken as an indictment of reserves, but rather a call for clear analyses and communication of the real impacts of reserves to fishing communities. There are many documented benefits reserves can provide beyond fisheries, from providing conservation benefits and ecological resilience, to increased tourism potential. In addition, as in the overfished case modeled here, reserves can provide fishery benefits in the long-term.

It is imperative though that those engaged in the design and implementation of reserves carefully consider and communicate the short-term impacts of reserves on the economic well-being of affected fisheries. It is disingenuous to tell a community that a reserve will provide fishery benefits, but neglect to point out that those benefits may not accrue for over a decade. In addition, support and enforcement of a reserve may quickly dissipate if a reserve does not begin to provide net economic benefits to a community on the time scale fishermen were expecting. Discussing the timing and magnitude of benefits stemming from reserves allows stakeholders to directly confront the challenges, and consider what solutions may be on the table given their circumstances. Our results indicate that rather than focusing on eliminating short-term losses through careful design, or counting on future benefits to finance fishery improvement loans, more potential lies in helping communities increase the value of their catch to offset reserve induced losses. 

# Works Cited

